### 2013-08-30 Paper/ms.tex
Initial commit

\documentclass[useAMS,usenatbib]{mn2e}

\voffset=-0.8in

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{bbm}

% \onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Hierarchical Reverberation Mapping]
{Hierarchical Reverberation Mapping}

\author[Brewer and Elliott]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  Tom Elliott$^{1}$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\date{To be submitted to MNRAS Letters}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

\end{abstract}

\begin{keywords}

\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\section*{Acknowledgements}

\begin{thebibliography}{99}

\end{thebibliography}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-08-30 Paper/ms.tex
Hierarchical model reconstruction

@@
 \usepackage{bbm}
+
+% Bold symbols
+\renewcommand{\btheta}{\boldsymbol{\theta}}
+\newcommand{\bx}{\boldsymbol{x}}
 
@@
 
+\section{Combining Inferences About Multiple Objects}
+Consider a sample of $N$ objects, each of which has parameters $\theta_i$.
+The inference about object $i$ is described by a posterior distribution
+\begin{eqnarray}
+p(\theta_i | x_i) \propto \pi(\theta_i)p(x_i | \theta_i)\label{eq:individual}
+\end{eqnarray}
+We shall assume that this inference was carried out individually
+on each object $i$, all using a common prior $\pi(\theta_i)$. Rather than
+analysing all objects together, which can be very computationally expensive,
+we can use the posterior distributions from Equation~\ref{eq:individual}
+to reconstruct the results that would be obtained if we did analyse all
+objects together.
+
+In a hierarchical model, the posterior distribution for
+$\btheta = \{\theta_1, ..., \theta_N\}$ and some hyperparameters $\alpha$
+given the data 
+$\bx = \{x_1, ..., x_N\}$
+should actually be
+\begin{eqnarray}
+p(\alpha, \btheta | \bx) &\propto&
+p(\alpha)p(\btheta|\alpha)p(\bx | \btheta, \alpha)\\
+&=& p(\alpha)\prod_{i=1}^N f(\theta_i|\alpha)p(x_i | \theta_i)
+\end{eqnarray}
+
 \section*{Acknowledgements}

### 2013-08-30 Paper/ms.tex
Fine references

@@
 
+Recently, \citet{2012MNRAS.427.2701F, 2013MNRAS.434L..16F} introduced an
+innovative approach to reverberation mapping where the results from multiple
+AGN can be combined to yield inferences about the entire sample of AGN,
+despite the fact that the constraints on any individual AGN are poor.
+
 \section{Combining Inferences About Multiple Objects}
@@
 
+\section{The Inference for a Single Object}
+The posterior distribution for the lag of a single object $i$ is obtained
+by fitting the following model.
+
+\begin{eqnarray}
+blah
+\end{eqnarray}
+
+Note that this is already not the cross-correlation.
+
+\section{Demonstration on Simulated Data}
+
 \section*{Acknowledgements}
@@
 \begin{thebibliography}{99}
+\bibitem[\protect\citeauthoryear{Fine et al.}{2013}]{2013MNRAS.434L..16F} 
+Fine S., et al., 2013, MNRAS, 434, L16
+
+\bibitem[\protect\citeauthoryear{Fine et al.}{2012}]{2012MNRAS.427.2701F} 
+Fine S., et al., 2012, MNRAS, 427, 2701
 

### 2013-08-30 Paper/ms.tex
Hierarchical derivation

@@
 \usepackage{xspace}
-\usepackage{bbm}
+\usepackage{dsfont}
 
@@
 \end{eqnarray}
+The marginal posterior distribution for the hyperparameters $\alpha$ is
+
+\begin{eqnarray}
+p(\alpha | \bx) &=&
+\int p(\alpha, \btheta|\bx) \, d\btheta\\
+&\propto& p(\alpha)\int \prod_{i=1}^N f(\theta_i|\alpha)p(x_i | \theta_i) d^N\theta\\
+&\propto& p(\alpha) \prod_{i=1}^N \int f(\theta_i|\alpha)p(x_i | \theta_i) d\theta_i\\
+&\propto& p(\alpha) \prod_{i=1}^N \int \frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i) \pi(\theta_i)d\theta_i\\
+&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i)\right]
+\end{eqnarray}
+where the expectation is taken with respect to the individual object posterior
+of Equation~\ref{eq:individual}. This result enables us to reconstruct the
+posterior distribution for the hyperparameters even though the individual object
+inferences were made without the hierarchical structure in the prior.
 

### 2013-08-31 Paper/ms.tex
Some scattered writing

@@
   Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
-  Tom Elliott$^{1}$
+  Tom M. Elliott$^{1}$
   \medskip\\
@@
 \begin{abstract}
-
+Reverberation mapping (RM) is an important technique in studies of active
+galactic nuclei (AGN). The key idea of RM is to measure the time lag $\tau$
+between variations in the continuum emission from the accretion disc
+and subsequent response of the broad line region (BLR). The measurement of
+$\tau$ is typically used to estimate the physical size of the BLR and is
+combined with other measurements to estimate the black hole mass $M_{\rm BH}$.
+A major difficulty with RM campaigns is the large amount of data needed to
+measure $\tau$.
 \end{abstract}
@@
 
+There are deeper issues at play in reverberation mapping, for instance, the
+mean lag $\tau$ is not the same as the mean radius of the BLR distribution,
+and the mean lag $\tau$ is also not what the common cross-correlation
+techniques measures. In this letter we will ignore these complications.
+
 Recently, \citet{2012MNRAS.427.2701F, 2013MNRAS.434L..16F} introduced an
@@
 AGN can be combined to yield inferences about the entire sample of AGN,
-despite the fact that the constraints on any individual AGN are poor.
+despite the fact that the constraints on any individual AGN are poor. Rather
+than accurately measuring $\tau$ in a single object, it is possible to roughly
+measure $\tau$ for a large number of objects, and to infer properties about
+the distribution of $\tau$ values in the sample of objects (and hence in
+a broader population, if the sample can be considered representative).
+
+We implement this idea with a Bayesian hierarchical model
+\citep{2012arXiv1208.3036L}.
+These models are becoming increasingly common in astrophysics and have been
+used in a variety of different fields
+\citep[e.g.][]{extreme_deconvolution, loredo, kelly}.
 
@@
 
+The prior for the underlying time variation of the continuum emission is
+a continuous autoregressive process of order 1, or a CAR(1) model. These models
+have been studied extensively for AGN variability
+\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
+
 \section{Demonstration on Simulated Data}
@@
 \begin{thebibliography}{99}
+
+\bibitem[\protect\citeauthoryear{Bovy Jo, Hogg, 
+\& Roweis}{2011}]{extreme_deconvolution} Bovy Jo, Hogg D.~W., Roweis S.~T., 2011, AnApS, 5, 1657
+
 \bibitem[\protect\citeauthoryear{Fine et al.}{2013}]{2013MNRAS.434L..16F} 
@@
 
+\bibitem[\protect\citeauthoryear{Kelly}{2007}]{kelly} Kelly 
+B.~C., 2007, ApJ, 665, 1489
+
+\bibitem[\protect\citeauthoryear{Kelly, Bechtold, 
+\& Siemiginowska}{2009}]{2009ApJ...698..895K} Kelly B.~C., Bechtold J.,
+Siemiginowska A., 2009, ApJ, 698, 895
+
+\bibitem[\protect\citeauthoryear{Loredo}{2004}]{loredo} Loredo 
+T.~J., 2004, AIP Conference Series, 735, 195
+
+\bibitem[\protect\citeauthoryear{Loredo}{2012}]{2012arXiv1208.3036L} Loredo 
+T.~J., 2012, arXiv, arXiv:1208.3036
+
+\bibitem[\protect\citeauthoryear{Zu et al.}{2013}]{2013ApJ...765..106Z} Zu 
+Y., Kochanek C.~S., Koz{\l}owski S., Udalski A., 2013, ApJ, 765, 106
+
+\bibitem[\protect\citeauthoryear{Zu, Kochanek, 
+\& Peterson}{2011}]{2011ApJ...735...80Z} Zu Y., Kochanek C.~S., Peterson B.~M., 2011, ApJ, 735, 80
+
 \end{thebibliography}

### 2013-08-31 Paper/ms.tex
MCMC references
Abstract words

@@
 A major difficulty with RM campaigns is the large amount of data needed to
-measure $\tau$.
+measure $\tau$. Recently, several approaches have been suggested for reducing
+the cost of RM. One is to make less detailed measurements on a large sample
+of AGN, and then combine the results to infer something about the sample of
+AGN as a whole. In this letter we implement this method using a hierarchical
+Bayesian model and contrast this with the results from the previous stacked
+cross-correlation technique. We find ...
 \end{abstract}
@@
 
+For the MCMC we used STAN \citep{nuts} and DNest \citep{dnest}.
+
 \section{Demonstration on Simulated Data}
@@
 \& Roweis}{2011}]{extreme_deconvolution} Bovy Jo, Hogg D.~W., Roweis S.~T., 2011, AnApS, 5, 1657
+
+\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
+\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B.,
+Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
 
@@
 
+\bibitem[\protect\citeauthoryear{Hoffman 
+\& Gelman}{2011}]{nuts} Hoffman M.~D., Gelman A., 2011, arXiv, arXiv:1111.4246
+
 \bibitem[\protect\citeauthoryear{Zu et al.}{2013}]{2013ApJ...765..106Z} Zu 

### 2013-08-31 Paper/ms.tex
Writing, equations

@@
 
-There are deeper issues at play in reverberation mapping, for instance, the
-mean lag $\tau$ is not the same as the mean radius of the BLR distribution,
-and the mean lag $\tau$ is also not what the common cross-correlation
-techniques measures. In this letter we will ignore these complications.
+There are deeper issues at play in reverberation mapping, that we will ignore
+for the purposes of this letter. We list them here for completeness. Firstly,
+the mean lag $\tau$ is not equal to $c$ times the mean radius of the BLR
+distribution. Secondly, the mean lag $\tau$ is also not what the common
+cross-correlation techniques measures, except in the case of very narrow
+transfer functions.
+
+If the continuum light curve is described by a function $y(t)$, then the line
+light curve $l(t)$ is given by
+\begin{eqnarray}
+l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) - B\right] \, d\tau
+\end{eqnarray}
+where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
+and $A$ and $B$ are response
+coefficients. The idea of reverberation mapping is to use noisy measurements
+of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
+of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
 
@@
 
-\section{The Inference for a Single Object}
-The posterior distribution for the lag of a single object $i$ is obtained
-by fitting the following model.
-
+\section{The Single Object Model}
+The posterior distribution for the mean lag $\bar{\tau}$ of a single object
+$i$ is obtained
+by fitting the following model. We assume, for simplicity, that
+the transfer function is uniform
+between limits $a$ and $b$, where $b > a$:
 \begin{eqnarray}
-blah
+\Psi(\tau) &=& \left\{
+\begin{array}{lr}
+\frac{1}{b-a}, & \tau \in [a,b]\\
+0, & \textnormal{otherwise}s
+\end{array}\right.
 \end{eqnarray}
-
-Note that this is already not the cross-correlation.
+and our goal is to measure the mean lag $\bar{\tau} = \frac{1}{2}(b-a)$.
 
@@
 \citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
+Note that inferring $\bar{\tau}$ from the data requires that we
+marginalise over an infinite number of nuisance parameters describing the
+behaviour of $y(t)$ at unobserved times. This marginalisation can be done
+either analytically or inside MCMC. We use the latter approach. We discretise
+time using ten time bins per day, and have a discrete continuum light curve
+$\mathbf{y} = \{y_1, ..., y_n\}$
+\begin{eqnarray}
+y_i = \mu + a\left(y_{i-1} - \mu\right) + \beta n_i
+\end{eqnarray}
+for $i \geq 2$, where the prior for the $\{n_i\}$ is independent standard
+normal distributions. This is the discrete AR(1) model from time series theory.
 
 For the MCMC we used STAN \citep{nuts} and DNest \citep{dnest}.
+
+Note the single-object model is already an improvement over standard
+cross-correlation techniques.
 

### 2013-08-31 Paper/ms.tex
Self references

@@
 cross-correlation techniques measures, except in the case of very narrow
-transfer functions.
+transfer functions. Some of these difficulties have been addressed in other
+contributions by \citet{pancoast} and \citet{arp151}.
 
@@
 marginalise over an infinite number of nuisance parameters describing the
-behaviour of $y(t)$ at unobserved times. This marginalisation can be done
+behaviour of $y(t)$ at unobserved times \citep{pancoast}.
+
+This marginalisation can be done
 either analytically or inside MCMC. We use the latter approach. We discretise
@@
 \& Roweis}{2011}]{extreme_deconvolution} Bovy Jo, Hogg D.~W., Roweis S.~T., 2011, AnApS, 5, 1657
+
+\bibitem[\protect\citeauthoryear{Brewer et al.}{2011}]{arp151} 
+Brewer B.~J., et al., 2011, ApJ, 733, L33
 
@@
 
+\bibitem[\protect\citeauthoryear{Pancoast, Brewer, 
+\& Treu}{2011}]{pancoast} Pancoast A., Brewer B.~J., Treu T., 2011, ApJ, 730, 139
+
 \bibitem[\protect\citeauthoryear{Zu et al.}{2013}]{2013ApJ...765..106Z} Zu 

### 2013-08-31 Paper/ms.tex
More self citations
Acknowledgements
likelihood

@@
 used in a variety of different fields
-\citep[e.g.][]{extreme_deconvolution, loredo, kelly}.
+\citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2013AJ....146....7B}.
 
@@
 
+For the likelihood (or sampling distribution, really the prior for the data
+given the parameters) we made the conventional gaussian assumption:
+\begin{eqnarray}
+Y_i &\sim& \mathcal{N}\left(y(t_{l_i}), \sigma_{y_i}^2\right)\\
+L_i &\sim& \mathcal{N}\left(l(t_{l_i}), \sigma_{l_i}^2\right)
+\end{eqnarray}
+
 For the MCMC we used STAN \citep{nuts} and DNest \citep{dnest}.
@@
 \section*{Acknowledgements}
+It is a pleasure to thank Tommaso Treu, Anna Pancoast (UCSB), and
+Brandon Kelly (UCSB) for many
+useful conversations about reverberation mapping. The STAN team
 
@@
 Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380
+
+\bibitem[\protect\citeauthoryear{Brewer, Foreman-Mackey, 
+\& Hogg}{2013}]{2013AJ....146....7B} Brewer B.~J., Foreman-Mackey D., Hogg D.~W., 2013, AJ, 146, 7
 

### 2013-09-10 Code/generate_data.py
Basic code for simulating data

@@ -1,0 +1,26 @@
+"""
+Program to generate simulated reverberation mapping data sets.
+"""
+
+import numpy as np
+import numpy.random as rng
+import matplotlib.pyplot as plt
+
+def ar1(y0=0., mu=0., L=200., beta=1., n=1000):
+	"""
+	Simulate a time series from an AR(1) distribution.
+	"""
+	alpha = np.exp(-1./L)
+
+	y = np.zeros(n)
+	for i in xrange(1, n):
+		y[i] = mu + alpha*(y[i-1] - mu) + beta*rng.randn()
+
+	return y
+
+
+if __name__ == '__main__':
+	y = ar1()
+	plt.plot(y)
+	plt.show()
+

### 2013-09-10 Code/Data.cpp
Copied code from other repo

@@ -1,0 +1,38 @@
+#include "Data.h"
+#include <fstream>
+
+using namespace std;
+
+Data Data::instance;
+
+Data::Data()
+{
+
+}
+
+void Data::load(const char* filename1, const char* filename2)
+{
+	t1.clear(); Y1.clear(); sig1.clear();
+
+	fstream fin;
+	fin.open(filename1, ios::in);
+	double temp1, temp2, temp3;
+	while(fin>>temp1 && fin>>temp2 && fin>>temp3)
+	{
+		t1.push_back((int)temp1);
+		Y1.push_back(temp2);
+		sig1.push_back(temp3);
+	}
+	fin.close();
+
+	t2.clear(); Y2.clear(); sig2.clear();
+	fin.open(filename2, ios::in);
+	while(fin>>temp1 && fin>>temp2 && fin>>temp3)
+	{
+		t2.push_back((int)temp1);
+		Y2.push_back(temp2);
+		sig2.push_back(temp3);
+	}
+	fin.close();
+}
+

### 2013-09-10 Code/Data.h

@@ -1,0 +1,37 @@
+#ifndef _Data_
+#define _Data_
+
+#include <vector>
+
+class Data
+{
+	private:
+		std::vector<int> t1, t2;
+		std::vector<double> Y1, Y2;
+		std::vector<double> sig1, sig2;
+
+	public:
+		Data();
+		void load(const char* filename1, const char* filename2);
+
+		// Accessors
+		int get_t1(int i) const { return t1[i]; }
+		double get_Y1(int i) const { return Y1[i]; }
+		double get_sig1(int i) const { return sig1[i]; }
+		int get_N1() const { return t1.size(); }
+		// Accessors
+		int get_t2(int i) const { return t2[i]; }
+		double get_Y2(int i) const { return Y2[i]; }
+		double get_sig2(int i) const { return sig2[i]; }
+		int get_N2() const { return t2.size(); }
+
+
+	private:
+		static Data instance;
+	public:
+		static Data& get_instance() { return instance; }
+
+};
+
+#endif
+

### 2013-09-10 Code/TimeSeriesModel.cpp

@@ -1,0 +1,183 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#include "TimeSeriesModel.h"
+#include "RandomNumberGenerator.h"
+#include "Utils.h"
+#include "Data.h"
+#include <cmath>
+
+using namespace std;
+using namespace DNest3;
+
+TimeSeriesModel::TimeSeriesModel()
+:n(1500), y(1500), y_response(Data::get_instance().get_N2())
+{
+
+}
+
+void TimeSeriesModel::fromPrior()
+{
+	alpha = 0.99 + 0.01*randomU();
+	beta = -log(randomU());
+	mu = 1000.*randn();
+	max_lag = 2.-100.*log(randomU());
+	K = 0.9*randomU();
+	A = -log(randomU());
+	B = 100.*randn();
+	for(size_t i=0; i<n.size(); i++)
+		n[i] = randn();
+	calculate_y();
+}
+
+double TimeSeriesModel::perturb()
+{
+	double logH = 0.;
+
+	int which = randInt(7);
+	if(which == 0)
+	{
+		logH -= 19.*log(alpha);
+		alpha += pow(10., 1.5 - 6.*randomU())*randn();
+		alpha = mod(alpha, 1.);
+		logH += 19.*log(alpha);
+	}
+	else if(which == 1)
+	{
+		beta = 1. - exp(-beta);
+		beta += pow(10., 1.5 - 6.*randomU())*randn();
+		beta = mod(beta, 1.);
[…]

### 2013-09-10 Code/TimeSeriesModel.h

@@ -1,0 +1,61 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#ifndef _TimeSeriesModel_
+#define _TimeSeriesModel_
+
+#include "Model.h"
+#include <vector>
+
+class TimeSeriesModel:public DNest3::Model
+{
+	private:
+		double alpha;
+		double beta;
+		double mu;
+		// Coefficients
+		double A, B;
+		std::vector<double> n, y, y_response;
+
+		// Lag stuff
+		double max_lag, K, min_lag;
+
+	public:
+		TimeSeriesModel();
+
+		// Generate the point from the prior
+		void fromPrior();
+
+		// Metropolis-Hastings proposals
+		double perturb();
+
+		void calculate_y();
+
+		// Likelihood function
+		double logLikelihood() const;
+
+		// Print to stream
+		void print(std::ostream& out) const;
+
+		// Return string with column information
+		std::string description() const;
+};
+
+#endif
+

### 2013-09-10 Code/display.py

@@ -1,0 +1,27 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+data1 = np.loadtxt('data1.txt')
+data2 = np.loadtxt('data2.txt')
+posterior_sample = np.atleast_2d(np.loadtxt('posterior_sample.txt'))
+
+points = 1500
+
+plt.ion()
+for i in xrange(0, posterior_sample.shape[0]):
+	plt.hold(False)
+	plt.errorbar(data1[:,0], data1[:,1], yerr=data1[:,2], fmt='ko')
+	plt.hold(True)
+	plt.plot(posterior_sample[i, 8:8+points], 'b', linewidth=2, alpha=0.5)
+	plt.errorbar(data2[:,0], data2[:,1], yerr=data2[:,2], fmt='go')
+	plt.plot(data2[:,0], posterior_sample[i, 8+points:], 'c', linewidth=2, alpha=0.5)
+	plt.xlabel('Time', fontsize=16)
+	plt.ylabel('$y$', fontsize=16)
+	plt.title((i+1))
+	plt.xlim([-0.5, 1000.5])
+	plt.ylim([-30., 100.])
+	plt.draw()
+
+plt.ioff()
+plt.show()
+

### 2013-09-10 Code/generate_data.py

@@ -1,26 +1,0 @@
-"""
-Program to generate simulated reverberation mapping data sets.
-"""
-
-import numpy as np
-import numpy.random as rng
-import matplotlib.pyplot as plt
-
-def ar1(y0=0., mu=0., L=200., beta=1., n=1000):
-	"""
-	Simulate a time series from an AR(1) distribution.
-	"""
-	alpha = np.exp(-1./L)
-
-	y = np.zeros(n)
-	for i in xrange(1, n):
-		y[i] = mu + alpha*(y[i-1] - mu) + beta*rng.randn()
-
-	return y
-
-
-if __name__ == '__main__':
-	y = ar1()
-	plt.plot(y)
-	plt.show()
-

### 2013-09-10 Code/get_object.py

@@ -1,0 +1,10 @@
+from pylab import *
+
+data1 = loadtxt('../../models/ts_simulations/objects/sim001.txt')
+data2 = loadtxt('../../models/ts_simulations/objects/sim001_line.txt')
+
+data1[:,0] *= 10
+data2[:,0] *= 10
+savetxt('data1.txt', data1)
+savetxt('data2.txt', data2)
+

### 2013-09-10 Code/main.cpp

@@ -1,0 +1,41 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#include <iostream>
+#include "Start.h"
+#include "Data.h"
+#include "TimeSeriesModel.h"
+
+using namespace std;
+using namespace DNest3;
+
+int main(int argc, char** argv)
+{
+	Data::get_instance().load("data1.txt", "data2.txt");
+
+	#ifndef DNest3_No_Boost
+	MTSampler<TimeSeriesModel> sampler = setup_mt<TimeSeriesModel>(argc, argv);
+	#else
+	Sampler<TimeSeriesModel> sampler = setup<TimeSeriesModel>(argc, argv);
+	#endif
+
+	sampler.run();
+	return 0;
+}
+

### 2013-09-10 Code/showresults.py

@@ -1,0 +1,4 @@
+import postprocess
+postprocess.postprocess(cut=0.3333)
+import display
+

### 2013-09-10 Code/simulate_data.py

@@ -1,0 +1,44 @@
+from pylab import *
+
+seed(123)
+
+# Make the first time series
+y1 = zeros(1000)
+for i in xrange(1, 1000):
+	y1[i] = 0.99*y1[i-1] + 1.*randn()
+y1 += 50.
+
+# Make the second time series
+a = 50
+b = 100
+y2 = zeros(1000)
+for i in xrange(500, 1000):
+	y2[i] = mean(y1[(i-b):(i-a)])
+y2 *= 0.5
+
+# Make datasets
+which1 = sort(randint(1000, size=100))
+which2 = 500 + sort(randint(500, size=100))
+
+sigma = 1.
+data1 = zeros((100, 3))
+data2 = zeros((100, 3))
+data1[:,0] = which1
+data1[:,1] = y1[which1] + sigma*randn(100)
+data1[:,2] = sigma
+
+data2[:,0] = which2
+data2[:,1] = y2[which2] + sigma*randn(100)
+data2[:,2] = sigma
+
+data2 = data2[array([20, 60, 80]), :]
+
+savetxt('data1.txt', data1)
+savetxt('data2.txt', data2)
+
+plot(y1, 'b')
+plot(y2, 'r')
+errorbar(data1[:,0], data1[:,1], yerr=data1[:,2], fmt='bo')
+errorbar(data2[:,0], data2[:,1], yerr=data2[:,2], fmt='ro')
+show()
+

### 2013-09-10 Code/get_object.py
Removed file

@@ -1,10 +1,0 @@
-from pylab import *
-
-data1 = loadtxt('../../models/ts_simulations/objects/sim001.txt')
-data2 = loadtxt('../../models/ts_simulations/objects/sim001_line.txt')
-
-data1[:,0] *= 10
-data2[:,0] *= 10
-savetxt('data1.txt', data1)
-savetxt('data2.txt', data2)
-

### 2013-09-10 Code/TimeSeriesModel.cpp
Rewrite of model

@@ -34,13 +34,13 @@ TimeSeriesModel::TimeSeriesModel()
 
 void TimeSeriesModel::fromPrior()
 {
-	alpha = 0.99 + 0.01*randomU();
-	beta = -log(randomU());
-	mu = 1000.*randn();
-	max_lag = 2.-100.*log(randomU());
-	K = 0.9*randomU();
-	A = -log(randomU());
-	B = 100.*randn();
+	L = exp(log(1.) + log(1E6)*randomU());
+	beta = exp(log(1E-3) + log(1E6)*randomU());
+	mu = 100.*tan(M_PI*(randomU() - 0.5));
+
+	max_lag = exp(log(1E-3) + log(1E3)*randomU());
+	K = randomU();
+
 	for(size_t i=0; i<n.size(); i++)
 		n[i] = randn();
 	calculate_y();
@@ -50,55 +50,41 @@ double TimeSeriesModel::perturb()
 {
 	double logH = 0.;
 
-	int which = randInt(7);
+	int which = randInt(5);
 	if(which == 0)
 	{
-		logH -= 19.*log(alpha);
-		alpha += pow(10., 1.5 - 6.*randomU())*randn();
-		alpha = mod(alpha, 1.);
-		logH += 19.*log(alpha);
+		L = log(L);
+		L += log(1E6)*pow(10., 1.5 - 6.*randomU())*randn();
+		L = mod(L - log(1.), log(1E6)) + log(1.);
+		L = exp(L);
 	}
 	else if(which == 1)
 	{
-		beta = 1. - exp(-beta);
-		beta += pow(10., 1.5 - 6.*randomU())*randn();
-		beta = mod(beta, 1.);
-		beta = -log(1. - beta);
+		beta = log(beta);
+		beta += log(1E6)*pow(10., 1.5 - 6.*randomU())*randn();
+		beta = mod(beta - log(1E-3), log(1E6)) + log(1E-3);
+		beta = exp(beta);
 	}
 	else if(which == 2)
 	{
-		logH -= -0.5*pow(mu/1000., 2);
-		mu += 1000.*pow(10., 1.5 - 6.*randomU())*randn();
-		logH += -0.5*pow(mu/1000., 2);
+		mu = atan(mu/100.)/M_PI + 0.5;
+		mu += pow(10., 1.5 - 6.*randomU())*randn();
+		mu = mod(mu, 1.);
+		mu = 100.*tan(M_PI*(mu - 0.5));
 	}
[…]

### 2013-09-10 Code/TimeSeriesModel.h

@@ -26,15 +26,17 @@
 class TimeSeriesModel:public DNest3::Model
 {
 	private:
-		double alpha;
+		// AR(1) stuff
+		double L;
 		double beta;
 		double mu;
+
 		// Coefficients
-		double A, B;
+		double A, C;
 		std::vector<double> n, y, y_response;
 
 		// Lag stuff
-		double max_lag, K, min_lag;
+		double max_lag, K;
 
 	public:
 		TimeSeriesModel();

### 2013-09-10 Code/TimeSeriesModel.cpp
Fixed up model, good OPTIONS

@@ -41,6 +41,9 @@ void TimeSeriesModel::fromPrior()
 	max_lag = exp(log(1E-3) + log(1E3)*randomU());
 	K = randomU();
 
+	A = exp(log(1E-3) + log(1E6)*randomU());
+	C = 100.*tan(M_PI*(randomU() - 0.5));	
+
 	for(size_t i=0; i<n.size(); i++)
 		n[i] = randn();
 	calculate_y();
@@ -50,7 +53,7 @@ double TimeSeriesModel::perturb()
 {
 	double logH = 0.;
 
-	int which = randInt(5);
+	int which = randInt(7);
 	if(which == 0)
 	{
 		L = log(L);
@@ -85,17 +88,37 @@ double TimeSeriesModel::perturb()
 		K += pow(10., 1.5 - 6.*randomU())*randn();
 		K = mod(K, 1.);
 	}
+	else if(which == 5)
+	{
+		A = log(A);
+		A += log(1E6)*pow(10., 1.5 - 6.*randomU())*randn();
+		A = mod(A - log(1E-3), log(1E6)) + log(1E-3);
+		A = exp(A);
+	}
+	else if(which == 6)
+	{
+		C = atan(C/100.)/M_PI + 0.5;
+		C += pow(10., 1.5 - 6.*randomU())*randn();
+		C = mod(C, 1.);
+		C = 100.*tan(M_PI*(C - 0.5));
+	}
 
 	// Always do this
 	double chance = pow(10., 0.5 - 4.*randomU());
 	double scale = pow(10., 1.5 - 6.*randomU());
+	bool full = randomU() <= 0.3;
 	for(size_t i=0; i<n.size(); i++)
 	{
 		if(randomU() <= chance)
 		{
-			logH -= -0.5*pow(n[i], 2);
-			n[i] += scale*randn();
-			logH += -0.5*pow(n[i], 2);
+			if(full)
+				n[i] = randn();
+			else
+			{
+				logH -= -0.5*pow(n[i], 2);
+				n[i] += scale*randn();
+				logH += -0.5*pow(n[i], 2);
+			}
 		}
 	}
 

### 2013-09-10 Code/TimeSeriesModel.cpp
Avoid division by zero, make many datasets

@@ -147,7 +147,7 @@ void TimeSeriesModel::calculate_y()
 	{
 		double tot = 0.;
 		int num = 0;
-		for(int j=(Data::get_instance().get_t2(i) - b); j<(Data::get_instance().get_t2(i) - a); j++)
+		for(int j=(Data::get_instance().get_t2(i) - b); j<(Data::get_instance().get_t2(i) - a + 1); j++)
 		{
 			if(j >= 0 && j < (int)y.size())
 			{

### 2013-09-10 Code/simulate_data.py

@@ -1,44 +1,53 @@
 from pylab import *
 
 seed(123)
+which = 0
 
-# Make the first time series
-y1 = zeros(1000)
-for i in xrange(1, 1000):
-	y1[i] = 0.99*y1[i-1] + 1.*randn()
-y1 += 50.
+for k in xrange(0, 100):
+	# Make the first time series
+	L = exp(log(100.) + log(100.)*rand())
+	alpha = exp(-1./L)
+	beta = exp(log(0.05) + log(20.)*rand())
 
-# Make the second time series
-a = 50
-b = 100
-y2 = zeros(1000)
-for i in xrange(500, 1000):
-	y2[i] = mean(y1[(i-b):(i-a)])
-y2 *= 0.5
+	y1 = zeros(1000)
+	for i in xrange(1, 1000):
+		y1[i] = alpha*y1[i-1] + beta*randn()
+	y1 += 50.
 
-# Make datasets
-which1 = sort(randint(1000, size=100))
-which2 = 500 + sort(randint(500, size=100))
+	# Make the second time series
+	b = exp(log(100.) + 0.3*randn())
+	a = rand()*b
+	tau = (a + b)/2.
+	if b >= 500.:
+		print('WARNING!')
 
-sigma = 1.
-data1 = zeros((100, 3))
-data2 = zeros((100, 3))
-data1[:,0] = which1
-data1[:,1] = y1[which1] + sigma*randn(100)
-data1[:,2] = sigma
+	y2 = zeros(1000)
+	for i in xrange(500, 1000):
+		y2[i] = mean(y1[(i-b):(i-a+1)])
+	y2 *= 0.5
 
-data2[:,0] = which2
-data2[:,1] = y2[which2] + sigma*randn(100)
-data2[:,2] = sigma
+	# Make datasets
+	which1 = sort(randint(1000, size=100))
+	which2 = 500 + sort(randint(500, size=2))
 
-data2 = data2[array([20, 60, 80]), :]
+	sigma1, sigma2 = 1., 1.
+	data1 = zeros((100, 3))
+	data2 = zeros((2, 3))
+	data1[:,0] = which1
+	data1[:,1] = y1[which1] + sigma1*randn(100)
+	data1[:,2] = sigma1
 
-savetxt('data1.txt', data1)
-savetxt('data2.txt', data2)
+	data2[:,0] = which2
[…]

### 2013-09-10 Paper/ms.tex
More references and words

@@
 \section{Introduction}
+Reverberation mapping (RM) is an important technique that has contributed a
+large amount to our knowledge of active galactic nuclei (AGN).
+
+Since its inception, there have been many improvements in the analysis of
+reverberation mapping data. These range from methods that attempt to infer the
+transfer function \citep{1995ApJ...440..166K, 2011ApJ...735...80Z},
+the velocity-resolved transfer function
+\citep{2010ApJ...720L..46B}, or the physical structure of the BLR itself
+\citep{pancoast, arp151}.
 
@@
 \begin{eqnarray}
-l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) - B\right] \, d\tau
+l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) - C\right] \, d\tau
 \end{eqnarray}
@@
 of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
+Throughout this letter we consider $y(t)$ and $l(t)$ as fluxes, not magnitudes.
 
@@
 \begin{thebibliography}{99}
+\bibitem[\protect\citeauthoryear{Bentz et al.}{2010}]{2010ApJ...720L..46B} 
+Bentz M.~C., et al., 2010, ApJ, 720, L46
 
@@
 
+\bibitem[\protect\citeauthoryear{Krolik 
+\& Done}{1995}]{1995ApJ...440..166K} Krolik J.~H., Done C., 1995, ApJ, 440, 166
+
 \bibitem[\protect\citeauthoryear{Loredo}{2004}]{loredo} Loredo 

### 2013-09-11 Paper/ms.tex
Fixed sign of C
Talk about the hierarchical prior

@@
 \begin{eqnarray}
-l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) - C\right] \, d\tau
+l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
 \end{eqnarray}
 where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
-and $A$ and $B$ are response
+and $A$ and $C$ are response
 coefficients. The idea of reverberation mapping is to use noisy measurements
@@
 to reconstruct the results that would be obtained if we did analyse all
-objects together.
+objects together with a hierarchical prior on the $\theta_i$ parameters.
 
-In a hierarchical model, the posterior distribution for
-$\btheta = \{\theta_1, ..., \theta_N\}$ and some hyperparameters $\alpha$
+In a hierarchical model, the prior for the parameters $\{\theta_i\}$ is created
+by introducing hyperparameters $\alpha$ such that the joint prior for $\alpha$
+and the $\{\theta_i\}$ is:
+\begin{eqnarray}
+p(\alpha, \theta_i) &=& p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha)
+\end{eqnarray}
+The posterior distribution for
+$\btheta = \{\theta_1, ..., \theta_N\}$ and the hyperparameters $\alpha$
 given the data 
@@
 The marginal posterior distribution for the hyperparameters $\alpha$ is
-
 \begin{eqnarray}

### 2013-09-12 Code/simulate_data.py
More variable qsos

@@ -7,7 +7,7 @@ for k in xrange(0, 100):
 	# Make the first time series
 	L = exp(log(100.) + log(100.)*rand())
 	alpha = exp(-1./L)
-	beta = exp(log(0.05) + log(20.)*rand())
+	beta = exp(log(0.2) + log(5.)*rand())
 
 	y1 = zeros(1000)
 	for i in xrange(1, 1000):

### 2013-09-12 Code/simulate_data.py
Calculate stacked CCF

@@ -1,7 +1,22 @@
 from pylab import *
 
+
+def ccf(t1, t2, y1, y2):
+	lags = empty(len(y1)*len(y2))
+	weights = empty(len(y1)*len(y2))
+	k = 0
+	for i in xrange(0, len(y1)):
+		for j in xrange(0, len(y2)):
+			lags[k] = t2[j] - t1[i]
+			weights[k] = y2[j]*y1[i]
+			k += 1
+	return [lags, weights]
+
 seed(123)
 which = 0
+
+all_lags = array([])
+all_weights = array([])
 
 for k in xrange(0, 100):
 	# Make the first time series
@@ -41,6 +56,10 @@ for k in xrange(0, 100):
 	data2[:,1] = y2[which2] + sigma2*randn(2)
 	data2[:,2] = sigma2
 
+	[lags, weights] = ccf(data1[:,0], data2[:,0], data1[:,1], data2[:,1])
+	all_lags = hstack([all_lags, lags])
+	all_weights = hstack([all_weights, weights/weights.sum()])
+
 	if k == which:
 		savetxt('data1.txt', data1)
 		savetxt('data2.txt', data2)
@@ -50,4 +69,7 @@ for k in xrange(0, 100):
 		errorbar(data1[:,0], data1[:,1], yerr=data1[:,2], fmt='bo')
 		errorbar(data2[:,0], data2[:,1], yerr=data2[:,2], fmt='ro')
 		show()
+
+hist(all_lags, 300, weights=all_weights)
+show()
 

### 2013-09-20 Code/run_all.py
Generate and run 100 objects

@@ -1,0 +1,81 @@
+from pylab import *
+
+def simulate_data(which=0, numpoints=5):
+	for k in xrange(0, 100):
+		# Make the first time series
+		L = exp(log(100.) + log(100.)*rand())
+		alpha = exp(-1./L)
+		beta = exp(log(0.2) + log(5.)*rand())
+
+		y1 = zeros(1000)
+		for i in xrange(1, 1000):
+			y1[i] = alpha*y1[i-1] + beta*randn()
+		y1 += 50.
+
+		# Make the second time series
+		b = exp(log(100.) + 0.3*randn())
+		a = rand()*b
+		tau = (a + b)/2.
+		if b >= 500.:
+			print('WARNING!')
+
+		y2 = zeros(1000)
+		for i in xrange(500, 1000):
+			y2[i] = mean(y1[(i-b):(i-a+1)])
+		y2 *= 0.5
+
+		# Make datasets
+		which1 = sort(randint(1000, size=100))
+		which2 = 500 + sort(randint(500, size=numpoints))
+
+		sigma1, sigma2 = 1., 1.
+		data1 = zeros((100, 3))
+		data2 = zeros((numpoints, 3))
+		data1[:,0] = which1
+		data1[:,1] = y1[which1] + sigma1*randn(100)
+		data1[:,2] = sigma1
+
+		data2[:,0] = which2
+		data2[:,1] = y2[which2] + sigma2*randn(numpoints)
+		data2[:,2] = sigma2
+
+		if k == which:
+			savetxt('data1.txt', data1)
+			savetxt('data2.txt', data2)
+
+import os
+seed(123)
+import postprocess
+
+for i in xrange(0, 1):
+	simulate_data(i, numpoints=5)
+
+	f = open('OPTIONS_TEMPLATE', 'r')
+	o = f.read()
+	f.close()
+
+	o = o.replace('XXX', '500')
+	o = o.replace('YYY', '500')
+	f = open('OPTIONS', 'w')
+	f.write(o)
+	f.close()
+
+	os.system('./main -t 8')
+		
+	l = loadtxt('levels.txt')
+	l = l[l[:,1] <= -30., :]
+
+	f = open('OPTIONS_TEMPLATE', 'r')
+	o = f.read()
+	f.close()
+
+	o = o.replace('XXX', str(l.shape[0]))
+	o = o.replace('YYY', '3000')
+	f = open('OPTIONS', 'w')
+	f.write(o)
+	f.close()
+
[…]

### 2013-09-20 Code/run_all.py
Don't plot

@@ -76,6 +76,6 @@ for i in xrange(0, 1):
 	f.close()
 
 	os.system('./main -t 8')
-	postprocess.postprocess(cut=0.3333)
+	postprocess.postprocess(cut=0.3333, plot=False)
 	os.system('cp posterior_sample.txt Results/' + str(i) + '.txt')
 

### 2013-09-20 Code/run_all.py
Actually run 100

@@ -47,7 +47,7 @@ import os
 seed(123)
 import postprocess
 
-for i in xrange(0, 1):
+for i in xrange(0, 100):
 	simulate_data(i, numpoints=5)
 
 	f = open('OPTIONS_TEMPLATE', 'r')

### 2013-09-23 Code/run_all.py
1% errors on second time series, two points, delete OPTIONS

@@ -28,7 +28,7 @@ def simulate_data(which=0, numpoints=5):
 		which1 = sort(randint(1000, size=100))
 		which2 = 500 + sort(randint(500, size=numpoints))
 
-		sigma1, sigma2 = 1., 1.
+		sigma1, sigma2 = 1., 0.25
 		data1 = zeros((100, 3))
 		data2 = zeros((numpoints, 3))
 		data1[:,0] = which1
@@ -48,7 +48,7 @@ seed(123)
 import postprocess
 
 for i in xrange(0, 100):
-	simulate_data(i, numpoints=5)
+	simulate_data(i, numpoints=2)
 
 	f = open('OPTIONS_TEMPLATE', 'r')
 	o = f.read()

### 2013-09-23 Code/simulate_data.py

@@ -45,7 +45,7 @@ for k in xrange(0, 100):
 	which1 = sort(randint(1000, size=100))
 	which2 = 500 + sort(randint(500, size=2))
 
-	sigma1, sigma2 = 1., 1.
+	sigma1, sigma2 = 1., 0.25
 	data1 = zeros((100, 3))
 	data2 = zeros((2, 3))
 	data1[:,0] = which1

### 2013-09-23 Code/Results/combine.py
Get posterior for hyperparameters

@@ -1,0 +1,36 @@
+from pylab import *
+
+def log_likelihood(params, xx):
+	mu, sigma = params[0], params[1]
+	logL = 0.
+	for x in xx:
+		f = 1./(sigma*sqrt(2.*pi))*exp(-0.5*((x - mu)/sigma)**2)
+		logL += log(mean(f))
+	return logL
+
+# Load all of the posterior samples
+xx = []
+for i in xrange(0, 100):
+	posterior_sample = atleast_2d(loadtxt(str(i) + '.txt'))
+	xx.append(log10(posterior_sample[:,0]))
+
+num = 512
+mu = linspace(-3., 3., num)
+sigma = linspace(0.01, 1., num)
+[mu, sigma] = meshgrid(mu, sigma)
+sigma = sigma[::-1, :]
+
+logL = zeros(mu.shape)
+for i in xrange(0, logL.shape[0]):
+	for j in xrange(0, logL.shape[1]):
+		logL[i, j] = log_likelihood([mu[i, j], sigma[i, j]], xx)
+	print(i)
+
+
+rc("font", size=16, family="serif", serif="Computer Sans")
+rc("text", usetex=True)
+imshow(exp(logL - logL.max()), aspect=6./0.99, extent=[-3, 3, 0.05, 1])
+xlabel('$\\mu$')
+ylabel('$\\sigma$')
+show()
+

### 2013-09-23 Code/Results/combine.py
Stay above sigma=0.05

@@ -16,7 +16,7 @@ for i in xrange(0, 100):
 
 num = 512
 mu = linspace(-3., 3., num)
-sigma = linspace(0.01, 1., num)
+sigma = linspace(0.05, 1., num)
 [mu, sigma] = meshgrid(mu, sigma)
 sigma = sigma[::-1, :]
 

### 2013-09-27 Code/Results/combine.py
Faster loading, plot true value, save figure

@@ -11,8 +11,8 @@ def log_likelihood(params, xx):
 # Load all of the posterior samples
 xx = []
 for i in xrange(0, 100):
-	posterior_sample = atleast_2d(loadtxt(str(i) + '.txt'))
-	xx.append(log10(posterior_sample[:,0]))
+	posterior_sample = loadtxt(str(i) + '.txt', usecols=[0])
+	xx.append(log10(posterior_sample))
 
 num = 512
 mu = linspace(-3., 3., num)
@@ -26,11 +26,12 @@ for i in xrange(0, logL.shape[0]):
 		logL[i, j] = log_likelihood([mu[i, j], sigma[i, j]], xx)
 	print(i)
 
-
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 imshow(exp(logL - logL.max()), aspect=6./0.99, extent=[-3, 3, 0.05, 1])
+plot(1.867, 0.157, 'wo')
 xlabel('$\\mu$')
 ylabel('$\\sigma$')
+savefig('posterior.eps', bbox_inches='tight')
 show()
 

### 2013-09-27 Code/Results/combine.py
Fix plot

@@ -29,9 +29,11 @@ for i in xrange(0, logL.shape[0]):
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 imshow(exp(logL - logL.max()), aspect=6./0.99, extent=[-3, 3, 0.05, 1])
-plot(1.867, 0.157, 'wo')
+hold(True)
+plot(1.867, 0.157, 'w*', markersize=10)
+ylim(0.05)
 xlabel('$\\mu$')
 ylabel('$\\sigma$')
-savefig('posterior.eps', bbox_inches='tight')
+savefig('posterior.pdf', bbox_inches='tight')
 show()
 

### 2013-09-27 Code/run_all.py
Compute ccf

@@ -1,6 +1,10 @@
 from pylab import *
 
 def simulate_data(which=0, numpoints=5):
+
+	lags = []
+	weights = []
+
 	for k in xrange(0, 100):
 		# Make the first time series
 		L = exp(log(100.) + log(100.)*rand())
@@ -42,6 +46,26 @@ def simulate_data(which=0, numpoints=5):
 		if k == which:
 			savetxt('data1.txt', data1)
 			savetxt('data2.txt', data2)
+
+		for ii in xrange(0, data1.shape[0]):
+			for jj in xrange(0, data2.shape[0]):
+				lags.append(data2[jj, 0] - data1[ii, 0])
+				weights.append((data1[ii, 1] - mean(data1[:,1]))*(data2[jj, 1] - mean(data2[:,1])))
+
+	lags = array(lags)
+	weights = array(weights)
+
+#	rc("font", size=16, family="serif", serif="Computer Sans")
+#	rc("text", usetex=True)
+
+
+#	hist(lags[abs(lags - 150) < 150], 300, weights=weights[abs(lags - 150) < 150], alpha=0.25)
+#	xlim([0, 300])
+#	ylim(-50)
+#	xlabel('Lag $\\tau$')
+#	ylabel('Stacked Cross-Correlation Function')
+#	savefig('ccf.pdf')
+#	show()
 
 import os
 seed(123)

### 2013-09-28 Paper/ms.tex
Fixed error
Working ont he abstract

@@
 \section{Introduction}
-Reverberation mapping (RM) is an important technique that has contributed a
-large amount to our knowledge of active galactic nuclei (AGN).
+Reverberation mapping (RM) is an important technique for the study
+of active galactic nuclei (AGN). The technique is based on the temporal
+fluctuations of the central continuum source, and the subsequent response
+of the broad line region (BLR) emission. The time delay between the continuum
+and the broad line fluctuations provides an estimate of the size of the BLR.
 
-Since its inception, there have been many improvements in the analysis of
-reverberation mapping data. These range from methods that attempt to infer the
-transfer function \citep{1995ApJ...440..166K, 2011ApJ...735...80Z},
+RM is a observationally intensive, requiring observations over a period of
+a few tens of days \citep{2013ApJ...769..128B}. As a result, many authors have
+studied the data analysis techniques involved in RM, and made substantial
+advances. These range from methods that attempt to infer the
+transfer function \citep[the distribution of lags in a single object,
+e.g.][]{1995ApJ...440..166K, 2011ApJ...735...80Z},
 the velocity-resolved transfer function
@@
 
-There are deeper issues at play in reverberation mapping, that we will ignore
-for the purposes of this letter. We list them here for completeness. Firstly,
-the mean lag $\tau$ is not equal to $c$ times the mean radius of the BLR
-distribution. Secondly, the mean lag $\tau$ is also not what the common
+There are many subtleties involved in reverberation mapping, that we will ignore
+for the purposes of this letter. We note them here for completeness. Firstly,
+the lag $\tau$ is not equal to $c$ times the mean radius of the BLR
+distribution. Secondly, the lag $\tau$ is also not what the common
 cross-correlation techniques measures, except in the case of very narrow
-transfer functions. Some of these difficulties have been addressed in other
+transfer functions (i.e. only a single lag in the system, rather than a wide
+distribution of lags). Some of these difficulties have been addressed in other
 contributions by \citet{pancoast} and \citet{arp151}.
@@
 &\propto& p(\alpha) \prod_{i=1}^N \int \frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i) \pi(\theta_i)d\theta_i\\
-&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i)\right]
+&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}\right]
 \end{eqnarray}
@@
 \begin{thebibliography}{99}
+\bibitem[\protect\citeauthoryear{Barth et al.}{2013}]{2013ApJ...769..128B} 
+Barth A.~J., et al., 2013, ApJ, 769, 128
+
 \bibitem[\protect\citeauthoryear{Bentz et al.}{2010}]{2010ApJ...720L..46B} 

### 2013-09-29 Paper/ms.tex
Figure
scale = 0.5
New figure (CCF), some work on text

@@
 for the purposes of this letter. We note them here for completeness. Firstly,
-the lag $\tau$ is not equal to $c$ times the mean radius of the BLR
-distribution. Secondly, the lag $\tau$ is also not what the common
-cross-correlation techniques measures, except in the case of very narrow
-transfer functions (i.e. only a single lag in the system, rather than a wide
-distribution of lags). Some of these difficulties have been addressed in other
-contributions by \citet{pancoast} and \citet{arp151}.
-
-If the continuum light curve is described by a function $y(t)$, then the line
-light curve $l(t)$ is given by
-\begin{eqnarray}
-l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
-\end{eqnarray}
-where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
-and $A$ and $C$ are response
-coefficients. The idea of reverberation mapping is to use noisy measurements
-of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
-of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
-Throughout this letter we consider $y(t)$ and $l(t)$ as fluxes, not magnitudes.
+the mean lag $\bar{\tau} = \int \Psi(\tau)\, d\tau$, where $\Psi(\tau)$
+is the transfer function, is not equal to $c$ times the mean radius of the BLR
+distribution. Secondly, the mean lag $\bar{\tau}$ is also not what is measured
+by the common
+cross-correlation technique, except in the case of very narrow
+transfer functions. Direct physical modelling of the BRL resolves these
+issues \citep{pancoast, arp151}.
 
@@
 \citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2013AJ....146....7B}.
+
+\section{Model Assumptions}
+
+If the continuum light curve is described by a function $y(t)$, then the line
+light curve $l(t)$ is given by
+\begin{eqnarray}
+l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
+\end{eqnarray}
+where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
+and $A$ and $C$ are response
+coefficients. The idea of reverberation mapping is to use noisy measurements
+of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
+of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
+Throughout this letter we consider $y(t)$ and $l(t)$ as fluxes, not magnitudes.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{Figures/posterior.eps}
+\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
+describing the distribution of $\bar{\tau}$ values in the sample. The prior
+distribution was uniform over the area shown.
+The true solution is indicated by the white circle.\label{fig:posterior}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{Figures/ccf.eps}
+\caption{The stacked cross-correlation function of the simulated data.
+\label{fig:ccf}}
+\end{center}
+\end{figure}
+
 \section*{Acknowledgements}

### 2013-09-29 Paper/ms.tex
Various edits

@@
 for the purposes of this letter. We note them here for completeness. Firstly,
-the mean lag $\bar{\tau} = \int \Psi(\tau)\, d\tau$, where $\Psi(\tau)$
-is the transfer function, is not equal to $c$ times the mean radius of the BLR
+the mean lag $\bar{\tau} = \int \tau\Psi(\tau)\, d\tau$, where $\Psi(\tau)$
+is the normalised transfer function, is not equal to $c$ times the mean radius of the BLR
 distribution. Secondly, the mean lag $\bar{\tau}$ is also not what is measured
@@
 of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
-Throughout this letter we consider $y(t)$ and $l(t)$ as fluxes, not magnitudes.
+Throughout this letter we consider $y(t)$ and $l(t)$ in flux
+units, as opposed to magnitudes.
 
@@
 where the expectation is taken with respect to the individual object posterior
-of Equation~\ref{eq:individual}. This result enables us to reconstruct the
+of Equation~\ref{eq:individual}, and thus can be estimated using posterior
+samples from the posterior distributions for the individual objects.
+This result enables us to reconstruct the
 posterior distribution for the hyperparameters even though the individual object
-inferences were made without the hierarchical structure in the prior.
+inferences were made without the hierarchical structure in the prior. This is
+essentially an importance sampling approximation to the hierarchical model.
 
@@
 The posterior distribution for the mean lag $\bar{\tau}$ of a single object
-$i$ is obtained
+$i$ may be obtained
 by fitting the following model. We assume, for simplicity, that
@@
 \end{eqnarray}
-and our goal is to measure the mean lag $\bar{\tau} = \frac{1}{2}(b-a)$.
+and our goal is to measure the mean lag:
+\begin{eqnarray}
+\bar{\tau} &=& \int \\
+&=& \frac{1}{2}(b-a)
+\end{eqnarray}
 
+Note that inferring $\bar{\tau}$ from the data requires that we
+marginalise over an infinite number of nuisance parameters describing the
+behaviour of $y(t)$ at unobserved times \citep{pancoast}.
 The prior for the underlying time variation of the continuum emission is
@@
 \citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
-Note that inferring $\bar{\tau}$ from the data requires that we
-marginalise over an infinite number of nuisance parameters describing the
-behaviour of $y(t)$ at unobserved times \citep{pancoast}.
-
 This marginalisation can be done
-either analytically or inside MCMC. We use the latter approach. We discretise
+either analytically or inside MCMC. We used the latter approach for simplicity.
+We discretised
 time using ten time bins per day, and have a discrete continuum light curve
@@
 normal distributions. This is the discrete AR(1) model from time series theory.
+$\mu$ describes the mean level of the continuum light curve, $\beta$ controls
+the size of the short-term fluctuations, and $a$ controls the correlation
+timescale.
 
@@
 
-For the MCMC we used STAN \citep{nuts} and DNest \citep{dnest}.
-
+To implement the MCMC we implemented this model in the STAN sampler \citep{nuts}
+and Diffusive Nested Sampling \citep{dnest}. Due to the large number of
+parameters and some very strong correlations in the posterior distribution,
+we found that Diffusive Nested Sampling was more effective than STAN.
 Note the single-object model is already an improvement over standard
-cross-correlation techniques.
+cross-correlation techniques and is similar to the approach used by
+\citep{2011ApJ...735...80Z}.
 
 \section{Demonstration on Simulated Data}
+To test our hierarchical model, and compare it to the stacked cross-correlation
+function, we simulated data from 100 AGN.
+
+The cross-correlation function for a single object is
 

### 2013-10-04 Paper/ms.tex
Working on it

@@
 is the normalised transfer function, is not equal to $c$ times the mean radius of the BLR
-distribution. Secondly, the mean lag $\bar{\tau}$ is also not what is measured
-by the common
+distribution, $\bar{r} = \int \sqrt{x^2+y^2+z^2}\rho(x, y, z)\, d^3 \mathbf{x}$.
+Secondly, the mean lag $\bar{\tau}$ is not accessible
+using the common
 cross-correlation technique, except in the case of very narrow
-transfer functions. Direct physical modelling of the BRL resolves these
+transfer functions.
+Direct physical modelling of the BLR resolves these
 issues \citep{pancoast, arp151}.
@@
 \begin{eqnarray}
-\bar{\tau} &=& \int \\
+\bar{\tau} &=& \int \tau \Psi(\tau) \, d\tau\\
 &=& \frac{1}{2}(b-a)
@@
 \begin{eqnarray}
-Y_i &\sim& \mathcal{N}\left(y(t_{l_i}), \sigma_{y_i}^2\right)\\
+Y_i &\sim& \mathcal{N}\left(y(t_{y_i}), \sigma_{y_i}^2\right)\\
 L_i &\sim& \mathcal{N}\left(l(t_{l_i}), \sigma_{l_i}^2\right)
@@
 
-To implement the MCMC we implemented this model in the STAN sampler \citep{nuts}
+To implement the MCMC for a single object,
+we implemented our model in the STAN sampler \citep{nuts}
 and Diffusive Nested Sampling \citep{dnest}. Due to the large number of
@@
 
-The cross-correlation function for a single object is
+The cross-correlation function for a single object is defined as
+
+\begin{eqnarray}
+\textnormal{CCF}(\tau) &=&
+\sum_{i=1}^{N_c} \sum_{j=1}^{N_l} \left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}\right)
+\delta\left[\tau - (t_{l_j} - t_{y_i})\right]
+\end{eqnarray}
+
+The stacked cross-correlation function for $N$ objects is the mean of the CCFs
+of the individual objects, after normalising each object's CCF to unity.
+
+\begin{eqnarray}
+\textnormal{SCCF}(\tau) &=&
+\frac{1}{N} \sum_{i=1}^N
+\left(
+\frac{\textnormal{CCF}_i(\tau)}{\int \textnormal{CCF}_i(\tau) \, d\tau}
+\right)
+\end{eqnarray}
 

### 2013-10-09 Paper/ms.tex
Defining CCF better

@@
 
-The cross-correlation function for a single object is defined as
+The cross-correlation function for a single object is defined as follows. First,
+the mean levels $\bar{y}$ and $\bar{l}$ of the continuum and line light curves,
+are calculated (weighted by the reported size of the error bars on each
+measurement):
+\begin{eqnarray}
+\bar{y} &=& \frac{\sum_{i=1}^{N_c} \left(y_i/\sigma_{y_i}^2\right)}{\sum_{i=1}^{N_c} \left(1/\sigma_{y_i}^2\right)}\\
+\bar{l} &=& \frac{\sum_{i=1}^{N_l} \left(l_i/\sigma_{l_i}^2\right)}{\sum_{i=1}^{N_l} \left(1/\sigma_{l_i}^2\right)}
+\end{eqnarray}
 
+The cross correlation function, as a function of lag $\tau$, is then defined as:
 \begin{eqnarray}
-\textnormal{CCF}(\tau) &=&
-\sum_{i=1}^{N_c} \sum_{j=1}^{N_l} \left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}\right)
-\delta\left[\tau - (t_{l_j} - t_{y_i})\right]
+\textnormal{CCF}(\tau) =
+\sum_{i=1}^{N_c} \sum_{j=1}^{N_l}
+\left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}
+\delta\left[\tau - (t_{l_j} - t_{y_i})\right]\right)
 \end{eqnarray}
+This can be understood as a set of delta-function spikes, one for each pair
+of points (one point chosen from the continuum data, and one point from the
+line data). The position of each spike depends on the time between the continuum
+data point and the line data point, and the mass of each spike is proportional
+to the continuum and line fluxes.
 

### 2013-10-10 Code/Results/combine.py
New figure

@@ -28,12 +28,35 @@ for i in xrange(0, logL.shape[0]):
 
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
-imshow(exp(logL - logL.max()), aspect=6./0.99, extent=[-3, 3, 0.05, 1])
+
+post = exp(logL - logL.max())
+post = post/post.sum()
+imshow(post, aspect=6./0.99, extent=[-3, 3, 0.05, 1])
 hold(True)
 plot(1.867, 0.157, 'w*', markersize=10)
 ylim(0.05)
 xlabel('$\\mu$')
 ylabel('$\\sigma$')
 savefig('posterior.pdf', bbox_inches='tight')
+show()
+
+figure(figsize=(10, 8))
+# Compute marginal posterior for mu
+# and predictive distribution for a new tau
+p = post.sum(axis=0)
+p /= trapz(p, x=mu[0, :])
+plot(mu[0, :], p, 'b', linewidth=2, label='Posterior distribution for $\\mu$')
+
+predictive = zeros(mu[0, :].shape)
+for i in xrange(0, post.shape[0]):
+	for j in xrange(0, post.shape[1]):
+		predictive += post[i, j]/(sigma[i, j]*sqrt(2.*pi))*exp(-0.5*((mu[0, :] - mu[i, j])/sigma[i, j])**2)
+
+plot(mu[0, :], predictive, 'r--', linewidth=2, label='Predictive distribution for new $\\bar{\\tau}$')
+xlim([0, 3])
+legend(loc = 'upper left')
+ylabel('Probability Density', fontsize=18)
+xlabel('$\\mu$,  log$_{10}(\\bar{\\tau})$', fontsize=20)
+savefig('posterior2.pdf', bbox_inches='tight')
 show()
 

### 2013-10-23 Code/run_all.py
New ccf figure (log tau)

@@ -52,17 +52,19 @@ def simulate_data(which=0, numpoints=5):
 				lags.append(data2[jj, 0] - data1[ii, 0])
 				weights.append((data1[ii, 1] - mean(data1[:,1]))*(data2[jj, 1] - mean(data2[:,1])))
 
-	lags = array(lags)
-	weights = array(weights)
+#	lags = array(lags)
+#	weights = array(weights)
 
 #	rc("font", size=16, family="serif", serif="Computer Sans")
 #	rc("text", usetex=True)
 
+#	_lags = lags[abs(lags - 150) < 150]
+#	_weights = weights[abs(lags - 150) < 150]
 
-#	hist(lags[abs(lags - 150) < 150], 300, weights=weights[abs(lags - 150) < 150], alpha=0.25)
-#	xlim([0, 300])
-#	ylim(-50)
-#	xlabel('Lag $\\tau$')
+#	hist(log10(_lags), 100, weights=_weights, alpha=0.25)
+#	xlim([0, 3])
+#	ylim(0)
+#	xlabel('$\\log_{10}(\\tau)$')
 #	ylabel('Stacked Cross-Correlation Function')
 #	savefig('ccf.pdf')
 #	show()

### 2013-10-24 Paper/ms.tex
Include extra plot
New version of ccf figure
Some new refs and words

@@
 A major difficulty with RM campaigns is the large amount of data needed to
-measure $\tau$. Recently, several approaches have been suggested for reducing
-the cost of RM. One is to make less detailed measurements on a large sample
-of AGN, and then combine the results to infer something about the sample of
-AGN as a whole. In this letter we implement this method using a hierarchical
+measure $\tau$. Recently, \citet{2012MNRAS.427.2701F} introduced a new approach
+to RM where the BLR light curve is sparsely sampled, but this is counteracted
+by observing a large sample of AGN, rather than a single system.
+The results are combined to infer properties of the sample of
+AGN. In this letter we implement this method using a hierarchical
 Bayesian model and contrast this with the results from the previous stacked
-cross-correlation technique. We find ...
+cross-correlation technique. We find that our inferences are more precise and
+allow for more straightforward interpretation than the cross-correlation
+technique.
 \end{abstract}
-
+galaxies:active --- methods: data analysis
 \begin{keywords}
@@
 of the broad line region (BLR) emission. The time delay between the continuum
-and the broad line fluctuations provides an estimate of the size of the BLR.
+and the broad line fluctuations provides an estimate of the size of the BLR
+\citep{peterson}.
 
@@
 a few tens of days \citep{2013ApJ...769..128B}. As a result, many authors have
-studied the data analysis techniques involved in RM, and made substantial
-advances. These range from methods that attempt to infer the
+studied the data analysis techniques involved in RM, and substantial
+advances have been made in recent years.
+The methods introduced range from those that attempt to infer the
 transfer function \citep[the distribution of lags in a single object,
@@
 \citep{2010ApJ...720L..46B}, or the physical structure of the BLR itself
-\citep{pancoast, arp151}.
+\citep{pancoast, arp151, pancoast2, 2013arXiv1310.3907L}.
 
@@
 distribution, $\bar{r} = \int \sqrt{x^2+y^2+z^2}\rho(x, y, z)\, d^3 \mathbf{x}$.
-Secondly, the mean lag $\bar{\tau}$ is not accessible
-using the common
-cross-correlation technique, except in the case of very narrow
-transfer functions.
-Direct physical modelling of the BLR resolves these
+Secondly, the mean lag $\bar{\tau}$ is not equivalent to the peak of the
+cross-correlation function, except in the case of very narrow
+transfer functions. Direct physical modelling of the BLR resolves these
 issues \citep{pancoast, arp151}.
@@
 used in a variety of different fields
-\citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2013AJ....146....7B}.
+\citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2013arXiv1310.5177B, 2013AJ....146....7B}.
 
@@
 \begin{center}
-\includegraphics[scale=0.5]{Figures/ccf.eps}
+\includegraphics[scale=0.35]{Figures/posterior2.eps}
+\caption{The marginal posterior distribution for $\mu$, the 
+hyperparameter describing the center of the distribution for
+$\log_{10}\left(\bar{\tau}\right)$, is plotted as the solid line.
+\label{fig:posterior2}}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/ccf.eps}
 \caption{The stacked cross-correlation function of the simulated data.
@@
 Brandon Kelly (UCSB) for many
-useful conversations about reverberation mapping. The STAN team
+useful conversations about reverberation mapping. The STAN ({\tt mc-stan.org})
+team provided helpful advice about the use of their software.
 
@@
 Bentz M.~C., et al., 2010, ApJ, 720, L46
-
-\bibitem[\protect\citeauthoryear{Bovy Jo, Hogg, 
-\& Roweis}{2011}]{extreme_deconvolution} Bovy Jo, Hogg D.~W., Roweis S.~T., 2011, AnApS, 5, 1657
 
@@
 
+\bibitem[\protect\citeauthoryear{Brewer et al.}{2013}]{2013arXiv1310.5177B} 
+Brewer B.~J., Marshall P.~J., Auger M.~W., Treu T., Dutton A.~A., 
+Barnab{\`e} M., 2013, arXiv, arXiv:1310.5177
+
 \bibitem[\protect\citeauthoryear{Fine et al.}{2013}]{2013MNRAS.434L..16F} 
@@
 Fine S., et al., 2012, MNRAS, 427, 2701
+
+\bibitem[\protect\citeauthoryear{Hogg, Myers, 
+\& Bovy}{2010}]{extreme_deconvolution} Hogg D.~W., Myers A.~D., Bovy J., 2010, ApJ, 725, 2166
 
@@
 \& Done}{1995}]{1995ApJ...440..166K} Krolik J.~H., Done C., 1995, ApJ, 440, 166
+
+\bibitem[\protect\citeauthoryear{Li et al.}{2013}]{2013arXiv1310.3907L} Li 
+Y.-R., Wang J.-M., Ho L.~C., Du P., Bai J.-M., 2013, arXiv, arXiv:1310.3907
 
@@
 
+\bibitem[\protect\citeauthoryear{Pancoast et 
+al.}{2012}]{pancoast2} Pancoast A., et al., 2012, ApJ, 754, 49
+
+\bibitem[\protect\citeauthoryear{Peterson}{2008}]{peterson} 
+Peterson B.~M., 2008, NewAR, 52, 240
+
 \bibitem[\protect\citeauthoryear{Zu et al.}{2013}]{2013ApJ...765..106Z} Zu 

### 2013-10-24 Paper/ms.tex
One more ref

@@
 used in a variety of different fields
-\citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2013arXiv1310.5177B, 2013AJ....146....7B}.
+\citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2012AJ....143...90S, 2013arXiv1310.5177B, 2013AJ....146....7B}.
 
@@
 
+\bibitem[\protect\citeauthoryear{Shu et al.}{2012}]{2012AJ....143...90S} 
+Shu Y., Bolton A.~S., Schlegel D.~J., Dawson K.~S., Wake D.~A., Brownstein 
+J.~R., Brinkmann J., Weaver B.~A., 2012, AJ, 143, 90
+
 \bibitem[\protect\citeauthoryear{Zu et al.}{2013}]{2013ApJ...765..106Z} Zu 

### 2013-10-24 Paper/ms.tex
Minor edits

@@
 used in a variety of different fields
-\citep[e.g.][]{extreme_deconvolution, loredo, kelly, 2012AJ....143...90S, 2013arXiv1310.5177B, 2013AJ....146....7B}.
+\citep[e.g.][]{loredo, kelly, extreme_deconvolution, 2012AJ....143...90S, 2013arXiv1310.5177B, 2013AJ....146....7B}.
 
 \section{Model Assumptions}
-
-If the continuum light curve is described by a function $y(t)$, then the line
+If the continuum light curve of an AGN
+is described by a function $y(t)$, then the line
 light curve $l(t)$ is given by
@@
 time using ten time bins per day, and have a discrete continuum light curve
-$\mathbf{y} = \{y_1, ..., y_n\}$
+$\mathbf{y} = \{y_1, ..., y_n\}$, included in the model as a set of unknown
+parameters. The prior for these parameters is:
 \begin{eqnarray}
-y_i = \mu + a\left(y_{i-1} - \mu\right) + \beta n_i
+p(y_i | y_{i-1},  \mu, a, \beta) \sim \mathcal{N}
+\left(\mu + a\left(y_{i-1} - \mu\right), \beta^2\right)
 \end{eqnarray}
-for $i \geq 2$, where the prior for the $\{n_i\}$ is independent standard
-normal distributions. This is the discrete AR(1) model from time series theory.
+for $i \geq 2$. This is the discrete AR(1) model from time series theory.
 $\mu$ describes the mean level of the continuum light curve, $\beta$ controls
@@
 useful conversations about reverberation mapping. The STAN ({\tt mc-stan.org})
-team provided helpful advice about the use of their software.
+team provided helpful advice about the use of their software. BJB is partially
+supported by the Marsden Fund (Royal Society of New Zealand).
 

### 2013-10-24 Code/run_all.py
New figure (show the data)

@@ -1,5 +1,9 @@
 from pylab import *
 
+
+rc("font", size=16, family="serif", serif="Computer Sans")
+rc("text", usetex=True)
+
 def simulate_data(which=0, numpoints=5):
 
 	lags = []
@@ -52,11 +56,24 @@ def simulate_data(which=0, numpoints=5):
 				lags.append(data2[jj, 0] - data1[ii, 0])
 				weights.append((data1[ii, 1] - mean(data1[:,1]))*(data2[jj, 1] - mean(data2[:,1])))
 
+#		if k < 3:
+#			subplot(3, 1, k+1)
+#			errorbar(data1[:,0]/10, data1[:,1], yerr=data1[:,2], fmt='bo', markersize=1, label='Continuum')
+#			errorbar(data2[:,0]/10, data2[:,1], yerr=data2[:,2], fmt='ro', markersize=1, label='Line')
+#			gca().set_yticks([0, 20, 40, 60])
+
+#			if k == 1:
+#				ylabel('Flux')
+#			if k < 2:
+#				gca().set_xticks([])
+#			else:
+#				xlabel('Time (days)')
+#				legend(loc='lower left', numpoints=1)
+#				savefig('data.pdf', bbox_inches='tight')
+#				show()
+
 #	lags = array(lags)
 #	weights = array(weights)
-
-#	rc("font", size=16, family="serif", serif="Computer Sans")
-#	rc("text", usetex=True)
 
 #	_lags = lags[abs(lags - 150) < 150]
 #	_weights = weights[abs(lags - 150) < 150]

### 2013-10-24 Code/run_all.py
Use days as units

@@ -78,12 +78,12 @@ def simulate_data(which=0, numpoints=5):
 #	_lags = lags[abs(lags - 150) < 150]
 #	_weights = weights[abs(lags - 150) < 150]
 
-#	hist(log10(_lags), 100, weights=_weights, alpha=0.25)
-#	xlim([0, 3])
+#	hist(log10(_lags/10), 100, weights=_weights, alpha=0.25)
+#	xlim([0, 1.5])
 #	ylim(0)
-#	xlabel('$\\log_{10}(\\tau)$')
+#	xlabel('$\\log_{10}(\\tau/(\\textnormal{1 day}))$')
 #	ylabel('Stacked Cross-Correlation Function')
-#	savefig('ccf.pdf')
+#	savefig('ccf.pdf', bbox_inches='tight')
 #	show()
 
 import os

### 2013-10-24 Code/Results/combine.py
New figures (days as units, grey color)

@@ -12,10 +12,10 @@ def log_likelihood(params, xx):
 xx = []
 for i in xrange(0, 100):
 	posterior_sample = loadtxt(str(i) + '.txt', usecols=[0])
-	xx.append(log10(posterior_sample))
+	xx.append(log10(posterior_sample/10.))
 
 num = 512
-mu = linspace(-3., 3., num)
+mu = linspace(-2., 2., num)
 sigma = linspace(0.05, 1., num)
 [mu, sigma] = meshgrid(mu, sigma)
 sigma = sigma[::-1, :]
@@ -31,9 +31,9 @@ rc("text", usetex=True)
 
 post = exp(logL - logL.max())
 post = post/post.sum()
-imshow(post, aspect=6./0.99, extent=[-3, 3, 0.05, 1])
+imshow(-post, aspect=4./0.99, extent=[-2, 2, 0.05, 1], cmap='gray')
 hold(True)
-plot(1.867, 0.157, 'w*', markersize=10)
+plot(0.867, 0.157, 'w*', markersize=10)
 ylim(0.05)
 xlabel('$\\mu$')
 ylabel('$\\sigma$')
@@ -53,10 +53,10 @@ for i in xrange(0, post.shape[0]):
 		predictive += post[i, j]/(sigma[i, j]*sqrt(2.*pi))*exp(-0.5*((mu[0, :] - mu[i, j])/sigma[i, j])**2)
 
 plot(mu[0, :], predictive, 'r--', linewidth=2, label='Predictive distribution for new $\\bar{\\tau}$')
-xlim([0, 3])
+xlim([-2, 2])
 legend(loc = 'upper left')
 ylabel('Probability Density', fontsize=18)
-xlabel('$\\mu$,  log$_{10}(\\bar{\\tau})$', fontsize=20)
+xlabel('$\\mu$,  log$_{10}(\\bar{\\tau}/(\\textnormal{1 day}))$', fontsize=20)
 savefig('posterior2.pdf', bbox_inches='tight')
 show()
 

### 2013-10-24 Paper/ms.tex
New figure (show the data)
Random writing

@@
 Consider a sample of $N$ objects, each of which has parameters $\theta_i$.
-The inference about object $i$ is described by a posterior distribution
+If the $i$th object is analysed on its own, the inference about 
+its parameters $\theta_i$ is described by a posterior distribution
 \begin{eqnarray}
@@
 \end{eqnarray}
-We shall assume that this inference was carried out individually
-on each object $i$, all using a common prior $\pi(\theta_i)$. Rather than
-analysing all objects together, which can be very computationally expensive,
-we can use the posterior distributions from Equation~\ref{eq:individual}
-to reconstruct the results that would be obtained if we did analyse all
-objects together with a hierarchical prior on the $\theta_i$ parameters.
+where $\pi(\theta_i)$ is the prior distribution and $p(x_i | \theta_i)$ is the
+likelihood function. If $N$ objects are analysed separately, inferences can
+be made about the diversity of $\theta_i$ across the sample. However, these
+inferences may be incorrect due to the implicit assumption that the prior for
+all of the $\{\theta_i\}$ is independent.
+A hierarchical model may be used to overcome this problem.
+Section~\ref{sec:single_object} describes the assumptions used for analysing
+data from a single AGN.
 
@@
 
-\section{The Single Object Model}
+Rather than
+analysing all objects together, which can be very computationally expensive,
+we can use the posterior distributions from Equation~\ref{eq:individual}
+to reconstruct the results that would be obtained if we did analyse all
+objects together with a hierarchical prior on the $\theta_i$ parameters.
+
+\section{The Single Object Model}\label{sec:single_object}
 The posterior distribution for the mean lag $\bar{\tau}$ of a single object
@@
 To test our hierarchical model, and compare it to the stacked cross-correlation
-function, we simulated data from 100 AGN.
+function, we simulated data from 100 AGN. The data for each object was
+continuum flux measurements, once per day, for 100 days. The continuum fluxes
+for each object oscillate around a mean value of 50 in arbitrary units, and the
+standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
+only two days, with times selected from a uniform distribution between $t=50$
+and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
+The flux of the line data is scaled to half that of the line data, and the
+measurement noise is 0.25, or 1\%, on the line data. See Figure~\ref{fig:data}
+for three illustrative data sets from the sample.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{Figures/data.eps}
+\caption{Three simulated data sets, out of a total of 100.\label{fig:data}}
+\end{center}
+\end{figure}
 
@@
 of the individual objects, after normalising each object's CCF to unity.
-
 \begin{eqnarray}
@@
 \end{eqnarray}
+Since the CCF definition involves delta-functions, some smoothing is necessary
+to display the stacked CCF. In Figure~\ref{fig:ccf},
+we show the stacked CCF from the 100 simulated AGN data sets, plotted as a
+histogram (the nonzero bin width provides the smoothing).
 

### 2013-10-25 Code/simulate_data.py
Removed old file

@@ -1,75 +1,0 @@
-from pylab import *
-
-
-def ccf(t1, t2, y1, y2):
-	lags = empty(len(y1)*len(y2))
-	weights = empty(len(y1)*len(y2))
-	k = 0
-	for i in xrange(0, len(y1)):
-		for j in xrange(0, len(y2)):
-			lags[k] = t2[j] - t1[i]
-			weights[k] = y2[j]*y1[i]
-			k += 1
-	return [lags, weights]
-
-seed(123)
-which = 0
-
-all_lags = array([])
-all_weights = array([])
-
-for k in xrange(0, 100):
-	# Make the first time series
-	L = exp(log(100.) + log(100.)*rand())
-	alpha = exp(-1./L)
-	beta = exp(log(0.2) + log(5.)*rand())
-
-	y1 = zeros(1000)
-	for i in xrange(1, 1000):
-		y1[i] = alpha*y1[i-1] + beta*randn()
-	y1 += 50.
-
-	# Make the second time series
-	b = exp(log(100.) + 0.3*randn())
-	a = rand()*b
-	tau = (a + b)/2.
-	if b >= 500.:
-		print('WARNING!')
-
-	y2 = zeros(1000)
-	for i in xrange(500, 1000):
-		y2[i] = mean(y1[(i-b):(i-a+1)])
-	y2 *= 0.5
-
-	# Make datasets
-	which1 = sort(randint(1000, size=100))
-	which2 = 500 + sort(randint(500, size=2))
-
-	sigma1, sigma2 = 1., 0.25
-	data1 = zeros((100, 3))
-	data2 = zeros((2, 3))
-	data1[:,0] = which1
-	data1[:,1] = y1[which1] + sigma1*randn(100)
-	data1[:,2] = sigma1
-
-	data2[:,0] = which2
-	data2[:,1] = y2[which2] + sigma2*randn(2)
-	data2[:,2] = sigma2
-
-	[lags, weights] = ccf(data1[:,0], data2[:,0], data1[:,1], data2[:,1])
-	all_lags = hstack([all_lags, lags])
-	all_weights = hstack([all_weights, weights/weights.sum()])
-
-	if k == which:
-		savetxt('data1.txt', data1)
-		savetxt('data2.txt', data2)
-
-		plot(y1, 'b')
-		plot(y2, 'r')
-		errorbar(data1[:,0], data1[:,1], yerr=data1[:,2], fmt='bo')
[…]

### 2013-10-25 Code/run_all.py
New CCF figure

@@ -1,13 +1,44 @@
 from pylab import *
 
-
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 
-def simulate_data(which=0, numpoints=5):
+def ccf(data1, data2, log10_tau, delta=0.1):
+	"""
+	Get the cross-correlation between log10_tau and log10_tau + delta
+	"""
+	s = 0.
+	c_bar = data1[:,1].mean()
 
-	lags = []
-	weights = []
+	nl = data2.shape[0]
+
+	# Loop over line measurements
+	for j in xrange(0, nl):
+
+		# Calculate mean line flux, excluding current point
+		which = ones(nl)
+		which[j] = 0.
+		which = which.astype('bool')
+		l_bar = data2[which,1].mean()
+
+		# Time difference between all continuum measurements
+		dd = data2[0,j] - data1[:,0]
+
+		# Find those within the bin
+		include = nonzero(logical_and(dd >= 10.**log10_tau,
+					dd < 10.**(log10_tau + delta)))[0]
+
+		if len(include) >= 1:
+			for ii in include:
+				s += ((nl - 1.)/nl*(data1[ii, 1] - c_bar)*
+						(data2[j, 1] - l_bar))/len(include)
+	return s
+
+
+
+def simulate_data(which=0, numpoints=5):
+#	log10_tau = linspace(-3, 3, 101)
+#	sccf = zeros(log10_tau.size)
 
 	for k in xrange(0, 100):
 		# Make the first time series
@@ -51,10 +82,18 @@ def simulate_data(which=0, numpoints=5):
 			savetxt('data1.txt', data1)
 			savetxt('data2.txt', data2)
 
-		for ii in xrange(0, data1.shape[0]):
-			for jj in xrange(0, data2.shape[0]):
-				lags.append(data2[jj, 0] - data1[ii, 0])
-				weights.append((data1[ii, 1] - mean(data1[:,1]))*(data2[jj, 1] - mean(data2[:,1])))
+#		for ii in xrange(0, log10_tau.size):
+#			sccf[ii] += ccf(data1, data2, log10_tau[ii],
+#					delta=log10_tau[1] - log10_tau[0])
+#		if k==99:
+#			bar(log10_tau - 1., sccf, width=log10_tau[1] - log10_tau[0],
+#						alpha=0.2)
[…]

### 2013-10-25 Paper/ms.tex
New CCF figure
Don't know what to say about ccf

@@
 
-The cross correlation function, as a function of lag $\tau$, is then defined as:
+The cross correlation function, as a function of lags $\tau$, is then defined as:
 \begin{eqnarray}
@@
 
-The stacked cross-correlation function for $N$ objects is the mean of the CCFs
-of the individual objects, after normalising each object's CCF to unity.
+The stacked cross-correlation function for $N$ objects is sum of the CCFs
+of the individual objects.
 \begin{eqnarray}
@@
 \end{eqnarray}
-Since the CCF definition involves delta-functions, some smoothing is necessary
-to display the stacked CCF. In Figure~\ref{fig:ccf},
-we show the stacked CCF from the 100 simulated AGN data sets, plotted as a
-histogram (the nonzero bin width provides the smoothing).
+In Figure~\ref{fig:ccf},
+we show the stacked CCF from the 100 simulated AGN data sets.
 

### 2013-10-26 Code/run_all.py
Fixed CCF bug

@@ -14,7 +14,6 @@ def ccf(data1, data2, log10_tau, delta=0.1):
 
 	# Loop over line measurements
 	for j in xrange(0, nl):
-
 		# Calculate mean line flux, excluding current point
 		which = ones(nl)
 		which[j] = 0.
@@ -22,7 +21,7 @@ def ccf(data1, data2, log10_tau, delta=0.1):
 		l_bar = data2[which,1].mean()
 
 		# Time difference between all continuum measurements
-		dd = data2[0,j] - data1[:,0]
+		dd = data2[j,0] - data1[:,0]
 
 		# Find those within the bin
 		include = nonzero(logical_and(dd >= 10.**log10_tau,
@@ -37,7 +36,7 @@ def ccf(data1, data2, log10_tau, delta=0.1):
 
 
 def simulate_data(which=0, numpoints=5):
-#	log10_tau = linspace(-3, 3, 101)
+#	log10_tau = linspace(-3, 3, 301)
 #	sccf = zeros(log10_tau.size)
 
 	for k in xrange(0, 100):
@@ -82,9 +81,12 @@ def simulate_data(which=0, numpoints=5):
 			savetxt('data1.txt', data1)
 			savetxt('data2.txt', data2)
 
+#		temp = zeros(log10_tau.size)
 #		for ii in xrange(0, log10_tau.size):
-#			sccf[ii] += ccf(data1, data2, log10_tau[ii],
+#			temp[ii] = ccf(data1, data2, log10_tau[ii],
 #					delta=log10_tau[1] - log10_tau[0])
+#		sccf += temp
+
 #		if k==99:
 #			bar(log10_tau - 1., sccf, width=log10_tau[1] - log10_tau[0],
 #						alpha=0.2)

### 2013-10-26 Paper/ms.tex
Trying to define the ccf...ugh

@@
 
-The cross-correlation function for a single object is defined as follows. First,
-the mean levels $\bar{y}$ and $\bar{l}$ of the continuum and line light curves,
-are calculated (weighted by the reported size of the error bars on each
-measurement):
+The cross-correlation function for a single object is defined as
+in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
+the amount of cross correlation is calculated using
 \begin{eqnarray}
-\bar{y} &=& \frac{\sum_{i=1}^{N_c} \left(y_i/\sigma_{y_i}^2\right)}{\sum_{i=1}^{N_c} \left(1/\sigma_{y_i}^2\right)}\\
-\bar{l} &=& \frac{\sum_{i=1}^{N_l} \left(l_i/\sigma_{l_i}^2\right)}{\sum_{i=1}^{N_l} \left(1/\sigma_{l_i}^2\right)}
+X \\= \sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
+\left(y_i - \bar{y}\right)
+\left(l_j - \bar{l}\right)
+\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)
 \end{eqnarray}
-
-The cross correlation function, as a function of lags $\tau$, is then defined as:
-\begin{eqnarray}
-\textnormal{CCF}(\tau) =
-\sum_{i=1}^{N_c} \sum_{j=1}^{N_l}
-\left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}
-\delta\left[\tau - (t_{l_j} - t_{y_i})\right]\right)
-\end{eqnarray}
-This can be understood as a set of delta-function spikes, one for each pair
-of points (one point chosen from the continuum data, and one point from the
-line data). The position of each spike depends on the time between the continuum
-data point and the line data point, and the mass of each spike is proportional
-to the continuum and line fluxes.
 

### 2013-10-27 Code/Results/example_posteriors.py
New figure

@@ -1,0 +1,28 @@
+from pylab import *
+
+# Plot the posterior samples for a few objects
+
+rc("font", size=16, family="serif", serif="Computer Sans")
+rc("text", usetex=True)
+
+bins = linspace(-4., 2., 31)
+
+for i in xrange(0, 3):
+	sample = loadtxt(str(i) + '.txt')
+	subplot(3,1,i+1)
+	hist(log10(sample[:,0]/10.), bins=bins, alpha=0.2, normed=True)
+
+	gca().set_yticks([])
+
+	if i < 2:
+		gca().set_xticklabels([])
+	else:
+		xlabel(r'$\log_{10}(\bar{\tau}/(\textnormal{1 day}))$')
+
+	if i==1:
+		ylabel('Posterior Probability')
+
+savefig('example_posteriors.pdf', bbox_inches='tight')
+show()
+
+

### 2013-10-27 Code/Results/example_posteriors.py
Tweaks to figures

@@ -7,6 +7,8 @@ rc("text", usetex=True)
 
 bins = linspace(-4., 2., 31)
 
+figure(figsize=(8, 9))
+
 for i in xrange(0, 3):
 	sample = loadtxt(str(i) + '.txt')
 	subplot(3,1,i+1)

### 2013-10-27 Code/run_all.py

@@ -97,10 +97,12 @@ def simulate_data(which=0, numpoints=5):
 #			savefig('ccf.pdf', bbox_inches='tight')
 #			show()
 
+#		if k==0:
+#			figure(figsize=(8, 9))
 #		if k < 3:
 #			subplot(3, 1, k+1)
-#			errorbar(data1[:,0]/10, data1[:,1], yerr=data1[:,2], fmt='bo', markersize=1, label='Continuum')
-#			errorbar(data2[:,0]/10, data2[:,1], yerr=data2[:,2], fmt='ro', markersize=1, label='Line')
+#			errorbar(data1[:,0]/10, data1[:,1], yerr=data1[:,2], fmt='bo', markersize=3, label='Continuum')
+#			errorbar(data2[:,0]/10, data2[:,1], yerr=data2[:,2], fmt='r*', markersize=5, label='Line')
 #			gca().set_yticks([0, 20, 40, 60])
 
 #			if k == 1:

### 2013-10-27 Paper/ms.tex
New figure
Working on ccf and figs

@@
 \end{abstract}
+
+\begin{keywords}
 galaxies:active --- methods: data analysis
-\begin{keywords}
-
 \end{keywords}
@@
 in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
-the amount of cross correlation is calculated using
+the amount of cross correlation is calculated by looping over pairs of points
+(one selected from the continuum data set, and another from the line data set),
+and accumulating mass when the lag between the two points is between $\tau$
+and $\tau + \delta$.
 \begin{eqnarray}
-X \\= \sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
+X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
 \left(y_i - \bar{y}\right)
 \left(l_j - \bar{l}\right)
-\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)
+\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
+{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
+\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
 \end{eqnarray}
+The denominator is the number of pairs of points that fall within the lag range
+being considered, $[\tau, \tau + \delta]$.
+The stacked cross-correlation function for $N$ objects is sum of the CCFs
+of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
+from our 100 simulated AGN data sets.
 
-The stacked cross-correlation function for $N$ objects is sum of the CCFs
-of the individual objects.
-\begin{eqnarray}
-\textnormal{SCCF}(\tau) &=&
-\frac{1}{N} \sum_{i=1}^N
-\left(
-\frac{\textnormal{CCF}_i(\tau)}{\int \textnormal{CCF}_i(\tau) \, d\tau}
-\right)
-\end{eqnarray}
-In Figure~\ref{fig:ccf},
-we show the stacked CCF from the 100 simulated AGN data sets.
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{Figures/example_posteriors.eps}
+\caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
+for three objects, each analysed separately with the single-object model. For
+the first object, there is a moderate ``detection'' of a lag at about 10 days.
+The second object yielded an upper limit, and the third object's lag was
+not well inferred.
+\label{fig:example_posteriors}}
+\end{center}
+\end{figure}
 

### 2013-10-27 Paper/ms.tex
Bunch of writing

@@
 
+We computed the stacked cross-correlation function for the 100 data sets.
 The cross-correlation function for a single object is defined as
@@
 The denominator is the number of pairs of points that fall within the lag range
-being considered, $[\tau, \tau + \delta]$.
+being considered, $[\tau, \tau + \delta]$, denoted $n_{\rm pair}$ by
+\citet{2012MNRAS.427.2701F}.
 The stacked cross-correlation function for $N$ objects is sum of the CCFs
 of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
-from our 100 simulated AGN data sets.
+from our 100 simulated AGN data sets. There is a clear peak around 10 days.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/ccf.eps}
+\caption{The stacked cross-correlation function of the simulated data.
+A clear peak is seen around $\tau \approx 10$ days, but the stacked CCF has a
+large width. It is difficult to interpret the cause of this width, and to
+determine whether the width is due to uncertainty or diversity in the sample
+of AGN. These difficulties motivate the hierarchical Bayesian model.
+\label{fig:ccf}}
+\end{center}
+\end{figure}
+
+As the data does not contain measurements at all possible time lags, the stacked
+CCF will always require some smoothing. Here, the smoothing is supplied by the
+choice of a bin width $\delta$. The stacked CCF has a substantial width. One
+weakness of the stacked CCF method is that it is not clear whether this width
+is caused by real diversity in the sample of AGN, or whether it is simply caused
+by the difficulty in measuring the lag $\bar{\tau}$ of an object with such
+sparse data. By contrast, the hierarchical Bayesian approach clearly separates
+these two concepts. The diversity of the population is quantified by $\sigma$,
+whereas uncertainty about the central value $\mu$ is described by the
+posterior distribution for $\mu$.
+
+To implement the hierarchical Bayesian approach on the simulated data, we first
+used the single-object model on each object. The results for three objects
+(the same three objects shown in Figure~\ref{fig:data}) are plotted in
+Figure~\ref{fig:example_posteriors}. Due to the sparse data, there is a large
+amount of uncertainty about the value of $\bar{\tau}$ for each system. Some
+objects do not allow any real measurement of $\bar{\tau}$, but some do, as a
+result of fortuitous variability of the continuum.
 
@@
 for three objects, each analysed separately with the single-object model. For
-the first object, there is a moderate ``detection'' of a lag at about 10 days.
+the first object, there is a moderate ``detection'' of a lag at about 10 days
+(although there is a small second mode above 100 days, which can be understood
+by inspecting the data in Figure~\ref{fig:data}).
 The second object yielded an upper limit, and the third object's lag was
@@
 \end{figure}
+
+Finally, we combined the results from the single-object model into an inference
+about hyperparameters $\mu$ and $\sigma$ describing the central value and
+the diversity of $\bar{\tau}$ respectively, using the result of
+Equation~\ref{eq:individual}. The joint posterior distribution for $\mu$ and
+$\sigma$ is shown in Figure~\ref{fig:posterior}. The prior for $\mu$ and $\sigma$
+was uniform inside the rectangle shown, and the posterior distribution covers
+a much smaller area, indicating that the data contained a lot of information
+about the hyperparameters.
 
@@
 distribution was uniform over the area shown.
-The true solution is indicated by the white circle.\label{fig:posterior}}
+The true solution is indicated by the white star symbol.\label{fig:posterior}}
 \end{center}
 \end{figure}
+
+The marginal distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
+along with the posterior predictive distribution for the ``next'' $\bar{\tau}$
+value.
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{Figures/ccf.eps}
-\caption{The stacked cross-correlation function of the simulated data.
-\label{fig:ccf}}
-\end{center}
-\end{figure}
+\section{Conclusions}
+Reverberation mapping is an important, yet observationally intensive, technique
+in studies of active galaxies.
 

### 2013-10-27 Code/Results/combine.py
Print summaries

@@ -47,6 +47,10 @@ p = post.sum(axis=0)
 p /= trapz(p, x=mu[0, :])
 plot(mu[0, :], p, 'b', linewidth=2, label='Posterior distribution for $\\mu$')
 
+m1 = trapz(p*mu[0, :], x=mu[0, :])
+m2 = trapz(p*mu[0, :]**2, x=mu[0, :])
+print(m1, sqrt(m2 - m1**2))
+
 predictive = zeros(mu[0, :].shape)
 for i in xrange(0, post.shape[0]):
 	for j in xrange(0, post.shape[1]):
@@ -58,5 +62,12 @@ legend(loc = 'upper left')
 ylabel('Probability Density', fontsize=18)
 xlabel('$\\mu$,  log$_{10}(\\bar{\\tau}/(\\textnormal{1 day}))$', fontsize=20)
 savefig('posterior2.pdf', bbox_inches='tight')
+
+
+m1 = trapz(predictive*mu[0, :], x=mu[0, :])
+m2 = trapz(predictive*mu[0, :]**2, x=mu[0, :])
+print(m1, sqrt(m2 - m1**2))
+
+
 show()
 

### 2013-10-29 Paper/ms.tex
Mention the summaries in paper
Going through intro

@@
 cross-correlation technique. We find that our inferences are more precise and
-allow for more straightforward interpretation than the cross-correlation
-technique.
+allow for more straightforward interpretation than the stacked cross-correlation
+results.
 \end{abstract}
@@
 of the broad line region (BLR) emission. The time delay between the continuum
-and the broad line fluctuations provides an estimate of the size of the BLR
-\citep{peterson}.
+and the broad line fluctuations provides an estimate of the size of the BLR,
+and can also be used to estimate the black hole mass \citep{peterson}.
 
-RM is a observationally intensive, requiring observations over a period of
+RM is a observationally intensive, requiring observations of an AGNN
+over a period of
 a few tens of days \citep{2013ApJ...769..128B}. As a result, many authors have
@@
 advances have been made in recent years.
-The methods introduced range from those that attempt to infer the
+The data analysis methods introduced range from those that attempt to infer the
 transfer function \citep[the distribution of lags in a single object,
@@
 
-There are many subtleties involved in reverberation mapping, that we will ignore
-for the purposes of this letter. We note them here for completeness. Firstly,
+There are many subtleties and challenges involved in reverberation mapping,
+that we will ignore
+for the purposes of this letter. We note two of them here for completeness. Firstly,
 the mean lag $\bar{\tau} = \int \tau\Psi(\tau)\, d\tau$, where $\Psi(\tau)$
@@
 transfer functions. Direct physical modelling of the BLR resolves these
-issues \citep{pancoast, arp151}.
+issues \citep{pancoast, arp151, 2013arXiv1310.3907L}.
 
@@
 than accurately measuring $\tau$ in a single object, it is possible to roughly
-measure $\tau$ for a large number of objects, and to infer properties about
+measure $\tau$ for a large number of objects (for example, by only measuring
+the BLR emission line flux at two epochs), and to infer properties about
 the distribution of $\tau$ values in the sample of objects (and hence in
 a broader population, if the sample can be considered representative).
+The data analysis approach of \citet{2012MNRAS.427.2701F} was based on an
+extension of the traditional cross-correlation method to $N$ separate objects.
+By ``stacking'' the cross-correlation functions (CCFs) from the $N$ objects in
+the sample, a peak appears which indicates a typical lag value in the sample
+of AGN. However, this peak is difficult to interpret. Specifically, the width
+of the peak may be influenced either by uncertainty (due to the sparse data)
+or due to a wide range of lags being present in the sample (i.e. the sample of
+AGN is diverse).
 
-We implement this idea with a Bayesian hierarchical model
-\citep{2012arXiv1208.3036L}.
-These models are becoming increasingly common in astrophysics and have been
-used in a variety of different fields
-\citep[e.g.][]{loredo, kelly, extreme_deconvolution, 2012AJ....143...90S, 2013arXiv1310.5177B, 2013AJ....146....7B}.
+In this letter, we revisit the idea of ``stacked'' reverberation mapping (i.e.
+using a sample of AGN with sparse data to infer something about the sample)
+from a Bayesian perspective. We develop a Bayesian hierarchical model
+\citep{loredo, kelly, extreme_deconvolution, 2012AJ....143...90S, 2012arXiv1208.3036L, 2013arXiv1310.5177B, 2013AJ....146....7B}.
+which allows us to measure
 
-\section{Model Assumptions}
-If the continuum light curve of an AGN
-is described by a function $y(t)$, then the line
-light curve $l(t)$ is given by
-\begin{eqnarray}
-l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
-\end{eqnarray}
-where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
-and $A$ and $C$ are response
-coefficients. The idea of reverberation mapping is to use noisy measurements
-of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
-of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
-Throughout this letter we consider $y(t)$ and $l(t)$ in flux
-units, as opposed to magnitudes.
+In Section~\ref{sec:multiple} we discuss the general principles needed
+to combine information from multiple poorly-measured objects.
+In Section~\ref{sec:single_object} we discuss the methods used to infer the lag
+$\tau$ using RM data for a single AGN. We then demonstrate the technique
+on simulated data in Section~\ref{sec:data}, and conclude in
+Section~\ref{sec:conclusions}.
 
-\section{Combining Inferences About Multiple Objects}
+\section{Combining Inferences About Multiple Objects}\label{sec:multiple}
 Consider a sample of $N$ objects, each of which has parameters $\theta_i$.
@@
 \section{The Single Object Model}\label{sec:single_object}
+
+\section{Model Assumptions}
+If the continuum light curve of an AGN
+is described by a function $y(t)$, then the line
+light curve $l(t)$ is given by
+\begin{eqnarray}
+l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) + C\right] \, d\tau
+\end{eqnarray}
+where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
+and $A$ and $C$ are response
+coefficients. The idea of reverberation mapping is to use noisy measurements
+of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
+of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.
+Throughout this letter we consider $y(t)$ and $l(t)$ in flux
+units, as opposed to magnitudes.
+
 The posterior distribution for the mean lag $\bar{\tau}$ of a single object
@@
 
-\section{Demonstration on Simulated Data}
+\section{Demonstration on Simulated Data}\label{sec:data}
 To test our hierarchical model, and compare it to the stacked cross-correlation
@@
 The marginal distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
-along with the posterior predictive distribution for the ``next'' $\bar{\tau}$
-value.
+along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
+$\mu = 0.892 \pm 0.033$, and the prediction about $\log_{10}(\bar{\tau})$
+may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$.
 
@@
 
-\section{Conclusions}
-Reverberation mapping is an important, yet observationally intensive, technique
-in studies of active galaxies.
+\section{Conclusions}\label{sec:conclusions}
+Reverberation mapping is an important, yet observationally intensive, technique in studies of active galaxies.
 

### 2013-10-29 Paper/ms.tex
More "scaffolding" type writing

@@
 inferences may be incorrect due to the implicit assumption that the prior for
-all of the $\{\theta_i\}$ is independent.
+all of the $\{\theta_i\}$ is independent \citep{2013arXiv1310.5177B}.
 A hierarchical model may be used to overcome this problem.
@@
 \end{eqnarray}
+The implied prior on the $\{\theta_i\}$ parameters is then
+\begin{eqnarray}
+p(\theta_i) &=& \int p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha) \, d\alpha
+\end{eqnarray}
+which may imply that the $\theta$ values are ``clustered'' around some
+typical value.
+
 The posterior distribution for
@@
 given the data 
-$\bx = \{x_1, ..., x_N\}$
-should actually be
+$\bx = \{x_1, ..., x_N\}$, is then
 \begin{eqnarray}
@@
 \end{eqnarray}
+
+It is possible to consider the data for all $N$ objects as one big data set
+and infer the parameters of all objects simultaneously. However, this can be
+computationally prohibitive. In some circumstances it is tractable to analyse
+each object's data separately (using a common prior $\pi(\theta_i)$) and
+then post-process the results, reconstructing what the results of the
+hierarchical model would have been. In this letter we use this approach.
+
 The marginal posterior distribution for the hyperparameters $\alpha$ is
@@
 &\propto& p(\alpha) \prod_{i=1}^N \int \frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i) \pi(\theta_i)d\theta_i\\
-&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}\right]
+&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}\right]\label{eq:combine}
 \end{eqnarray}
@@
 inferences were made without the hierarchical structure in the prior. This is
-essentially an importance sampling approximation to the hierarchical model.
+essentially an importance sampling approximation to the
+full hierarchical model.
 
-Rather than
-analysing all objects together, which can be very computationally expensive,
-we can use the posterior distributions from Equation~\ref{eq:individual}
-to reconstruct the results that would be obtained if we did analyse all
-objects together with a hierarchical prior on the $\theta_i$ parameters.
+In Section~\ref{sec:single_object} we define a simple model for inferring the
+lag of a single AGN from sparse RM data. We will use Markov Chain Monte Carlo
+(MCMC) to produce posterior samples for the lags of the $N$ objects, which can
+then be combined using Equation~\ref{eq:combine} to yield the posterior
+distribution for some hyperparameters describing the distribution of
+lags in the sample.
 
 \section{The Single Object Model}\label{sec:single_object}
-
-\section{Model Assumptions}
 If the continuum light curve of an AGN
@@
 Throughout this letter we consider $y(t)$ and $l(t)$ in flux
-units, as opposed to magnitudes.
+units, as opposed to magnitudes, and consider $\bar{\tau}$ as
+the definition of ``the lag'' of the AGN.
 
-The posterior distribution for the mean lag $\bar{\tau}$ of a single object
+The posterior distribution for the lag $\bar{\tau}$ of a single object
 $i$ may be obtained

### 2013-10-29 Paper/ms.tex
More writing...

@@
 the size of the short-term fluctuations, and $a$ controls the correlation
-timescale.
+timescale (the timescale is given by $L = -1/\log(a)$).
 
@@
 
+We chose a log-uniform prior for $L$ (the AGN variability timescale)
+between $1$ and $10^6$ days, a log-uniform
+prior for $\beta$ (the size of the short-term fluctuations)
+between $10^{-3}$ and $10^3$ flux units, a Cauchy(0, 100)
+prior for $\mu$ (the mean flux level of the AGN), a log-uniform prior for $b$
+(the upper limit of the transfer function) between $10^{-3}$ and $10^3$ days,
+a uniform prior for $a$ (the lower limit of the transfer function)
+between 0 and $b$, a log-uniform prior between
+$10^{-3}$ and $10^3$ for the response coefficient $A$ and a Cauchy(0, 100) prior
+for the second response parameter $C$.
+
 To implement the MCMC for a single object,
@@
 and Diffusive Nested Sampling \citep{dnest}. Due to the large number of
-parameters and some very strong correlations in the posterior distribution,
+parameters, multiple modes, and strong correlations in the posterior distribution,
 we found that Diffusive Nested Sampling was more effective than STAN.
-Note the single-object model is already an improvement over standard
+Note that our single-object model is already an improvement over standard
 cross-correlation techniques and is similar to the approach used by

### 2013-10-29 Paper/ms.tex
Conclusions etc

@@
 The flux of the line data is scaled to half that of the line data, and the
-measurement noise is 0.25, or 1\%, on the line data. See Figure~\ref{fig:data}
+measurement noise for the line data is 0.25, or 1\%. See Figure~\ref{fig:data}
 for three illustrative data sets from the sample.
@@
 \includegraphics[scale=0.5]{Figures/data.eps}
-\caption{Three simulated data sets, out of a total of 100.\label{fig:data}}
+\caption{Three simulated data sets, out of a total of 100. It is difficult to
+infer the lag $\bar{\tau}$ for any of these objects (although there is some
+information available). See Figure~\ref{fig:example_posteriors} for the
+$\bar{\tau}$ posterior distributions for these three data sets.
+\label{fig:data}}
 \end{center}
@@
 of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
-from our 100 simulated AGN data sets. There is a clear peak around 10 days.
+(on a log scale) from our 100 simulated AGN data sets.
+There is a clear peak around 10 days, and the full width at half maximum,
+while not strictly well defined, is roughly 0.25 dex.
 
@@
 sparse data. By contrast, the hierarchical Bayesian approach clearly separates
-these two concepts. The diversity of the population is quantified by $\sigma$,
-whereas uncertainty about the central value $\mu$ is described by the
-posterior distribution for $\mu$.
+these two concepts.
 
@@
 the diversity of $\bar{\tau}$ respectively, using the result of
-Equation~\ref{eq:individual}. The joint posterior distribution for $\mu$ and
-$\sigma$ is shown in Figure~\ref{fig:posterior}. The prior for $\mu$ and $\sigma$
+Equation~\ref{eq:individual}. Since lags $\bar{\tau}$ are positive, 
+our assumption for the prior on $\bar{\tau}$ given
+the hyperparameters is a lognormal distribution with median $\mu$ and
+width (standard deviation of $\log(\bar{\tau})$) $\sigma$:
+\begin{eqnarray}
+\log(\bar{\tau}) \sim \mathcal{N}(\log(\mu), \sigma^2)
+\end{eqnarray}
+
+The joint posterior distribution for $\mu$ and
+$\sigma$, given the data from $N=100$ AGN,
+is shown in Figure~\ref{fig:posterior}. The prior for $\mu$ and $\sigma$
 was uniform inside the rectangle shown, and the posterior distribution covers
 a much smaller area, indicating that the data contained a lot of information
-about the hyperparameters.
+about the hyperparameters. The true values used to generate the simulated data
+are denoted by the star symbol in Figure~\ref{fig:posterior},
+and is typical of the posterior distribution, as it should be.
 
@@
 
-The marginal distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
+The marginal posterior distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
 along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
 $\mu = 0.892 \pm 0.033$, and the prediction about $\log_{10}(\bar{\tau})$
-may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$.
+may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$. The Bayesian
+approach has clearly separated the uncertainty about $\mu$ from the diversity of the
+sample, described by $\sigma$.
 
@@
 \section{Conclusions}\label{sec:conclusions}
-Reverberation mapping is an important, yet observationally intensive, technique in studies of active galaxies.
+Reverberation mapping is an important, yet observationally intensive,
+technique in studies of active galaxies. This has motivated substantial
+research into RM data analysis techniques, as well as less costly observing
+strategies. The recent approach of \citet{2012MNRAS.427.2701F} demonstrated
+that it is possible to combine information from many sparsely-measured AGN
+and infer properties of the sample rather than insisting on accurate results
+about a particular object.
+
+In this letter we extended the approach of \citet{2012MNRAS.427.2701F} by
+implementing a Bayesian hierarchical model for the data analysis. The main
+advantage of this approach is a clear interpretation of the output, which is
+a posterior distribution for hyperparameters describing the sample of AGN.
+
+We demonstrated this approach on a simulated data set consisting of 100 AGN
+with well-measured continuum light curves but sparsely measured (two epochs per
+AGN) broad line light curves. For the simulated data set we were able to obtain
+an inference on $\mu$, a hyperparameter describing the typical value of the lag,
+to within 0.033 dex (1-$\sigma$ uncertainty), whereas the stacked cross-correlation
+function had a FWHM of $\sim$ 0.25 dex. This is possible because a subset of
+the objects in the sample will have a measureable lag. We hope this approach
+will facilitate informative studies of samples of AGN.
 

### 2013-10-29 Paper/ms.tex
Log base 10 where appropriate

@@
 the hyperparameters is a lognormal distribution with median $\mu$ and
-width (standard deviation of $\log(\bar{\tau})$) $\sigma$:
+width (standard deviation of $\log_{10}(\bar{\tau})$) $\sigma$:
 \begin{eqnarray}
-\log(\bar{\tau}) \sim \mathcal{N}(\log(\mu), \sigma^2)
+\log_{10}(\bar{\tau}) \sim \mathcal{N}(\log_{10}(\mu), \sigma^2)
 \end{eqnarray}

### 2013-10-29 Paper/ms.tex
ln

@@
 the size of the short-term fluctuations, and $a$ controls the correlation
-timescale (the timescale is given by $L = -1/\log(a)$).
+timescale (the timescale is given by $L = -1/\ln(a)$).
 

### 2013-10-30 Code/run_all.py
Use levels

@@ -147,7 +147,7 @@ for i in xrange(0, 100):
 	f.write(o)
 	f.close()
 
-	os.system('./main -t 8')
+	os.system('./main -t 8 -l levels.txt')
 	postprocess.postprocess(cut=0.3333, plot=False)
 	os.system('cp posterior_sample.txt Results/' + str(i) + '.txt')
 

### 2013-10-30 Code/run_all.py
Seed rng inside generate_data, for reproducibility

@@ -38,6 +38,7 @@ def ccf(data1, data2, log10_tau, delta=0.1):
 def simulate_data(which=0, numpoints=5):
 #	log10_tau = linspace(-3, 3, 301)
 #	sccf = zeros(log10_tau.size)
+	seed(123)
 
 	for k in xrange(0, 100):
 		# Make the first time series
@@ -116,7 +117,6 @@ def simulate_data(which=0, numpoints=5):
 #				show()
 
 import os
-seed(123)
 import postprocess
 
 for i in xrange(0, 100):

### 2013-10-30 Code/run_all.py
Seed dnest for reproducibility

@@ -132,7 +132,7 @@ for i in xrange(0, 100):
 	f.write(o)
 	f.close()
 
-	os.system('./main -t 8')
+	os.system('./main -t 8 -s 0')
 		
 	l = loadtxt('levels.txt')
 	l = l[l[:,1] <= -30., :]
@@ -147,7 +147,7 @@ for i in xrange(0, 100):
 	f.write(o)
 	f.close()
 
-	os.system('./main -t 8 -l levels.txt')
+	os.system('./main -t 8 -s 0 -l levels.txt')
 	postprocess.postprocess(cut=0.3333, plot=False)
 	os.system('cp posterior_sample.txt Results/' + str(i) + '.txt')
 

### 2013-10-30 Code/run_all.py
Slight efficiency tweaks

@@ -127,7 +127,7 @@ for i in xrange(0, 100):
 	f.close()
 
 	o = o.replace('XXX', '500')
-	o = o.replace('YYY', '500')
+	o = o.replace('YYY', '400')
 	f = open('OPTIONS', 'w')
 	f.write(o)
 	f.close()
@@ -148,6 +148,6 @@ for i in xrange(0, 100):
 	f.close()
 
 	os.system('./main -t 8 -s 0 -l levels.txt')
-	postprocess.postprocess(cut=0.3333, plot=False)
+	postprocess.postprocess(cut=0.25, plot=False)
 	os.system('cp posterior_sample.txt Results/' + str(i) + '.txt')
 

### 2013-10-30 Code/showresults.py
cut of 0.25

@@ -1,4 +1,4 @@
 import postprocess
-postprocess.postprocess(cut=0.3333)
+postprocess.postprocess(cut=0.25)
 import display
 

### 2013-10-30 Paper/ms.tex
Prior talk

@@
 
+We used vague priors for the parameters of the single-object model. In practice
+these could be made substantially narrower.
 We chose a log-uniform prior for $L$ (the AGN variability timescale)
-between $1$ and $10^6$ days, a log-uniform
+between $0.1$ and $10^5$ days, a log-uniform
 prior for $\beta$ (the size of the short-term fluctuations)
@@
 prior for $\mu$ (the mean flux level of the AGN), a log-uniform prior for $b$
-(the upper limit of the transfer function) between $10^{-3}$ and $10^3$ days,
+(the upper limit of the transfer function) between $10^{-4}$ and $10^2$ days,
 a uniform prior for $a$ (the lower limit of the transfer function)
@@
 the diversity of $\bar{\tau}$ respectively, using the result of
-Equation~\ref{eq:individual}. Since lags $\bar{\tau}$ are positive, 
+Equation~\ref{eq:individual}. This requires us to know the prior $\pi(\bar{\tau})$
+implied by the simple-object model, since we did not assign the prior directly
+to $\bar{\tau}$. The prior for $\bar{\tau}$ in the single-object model is
+very well approximated by a log-uniform distribution.
+
+Since lags $\bar{\tau}$ are positive, 
 our assumption for the prior on $\bar{\tau}$ given

### 2013-10-31 Code/Results/example_posteriors.py
Higher resolution, darker colour

@@ -5,15 +5,15 @@ from pylab import *
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 
-bins = linspace(-4., 2., 31)
+bins = linspace(-4., 2., 101)
 
 figure(figsize=(8, 9))
 
 for i in xrange(0, 3):
 	sample = loadtxt(str(i) + '.txt')
 	subplot(3,1,i+1)
-	hist(log10(sample[:,0]/10.), bins=bins, alpha=0.2, normed=True)
-
+	hist(log10(sample[:,0]/10.), bins=bins, normed=True)
+	xlim([-4, 2])
 	gca().set_yticks([])
 
 	if i < 2:

### 2013-10-31 Code/run_all.py
Color of histograms

@@ -89,8 +89,7 @@ def simulate_data(which=0, numpoints=5):
 #		sccf += temp
 
 #		if k==99:
-#			bar(log10_tau - 1., sccf, width=log10_tau[1] - log10_tau[0],
-#						alpha=0.2)
+#			bar(log10_tau - 1., sccf, width=log10_tau[1] - log10_tau[0])
 #			xlabel(r'$\log_{10}(\tau/(\textnormal{1 day}))$')
 #			ylabel('Stacked CCF')
 #			xlim([0, 2])

### 2013-11-01 Paper/ms.tex
New version of figure, with more samples
eqnarray --> align

@@
 and $\tau + \delta$.
-\begin{eqnarray}
-X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
+\begin{align}
+& X(\tau; \delta) = \nonumber \\
+& \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
 \left(y_i - \bar{y}\right)
@@
 \mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
-\end{eqnarray}
+\end{align}
 The denominator is the number of pairs of points that fall within the lag range
@@
 by inspecting the data in Figure~\ref{fig:data}).
-The second object yielded an upper limit, and the third object's lag was
-not well inferred.
+The second object's lag was not well constrained,
+and the third object's data only provided an upper limit on its lag.
 \label{fig:example_posteriors}}

### 2013-11-01 Paper/ms.tex
Slight wording change
Various edits

@@
 % Bold symbols
-\renewcommand{\btheta}{\boldsymbol{\theta}}
-\newcommand{\bx}{\boldsymbol{x}}
+\renewcommand{\btheta}{\{\theta_i\}}
+\newcommand{\bx}{\{x_i\}}
 
@@
 \section{Introduction}
-Reverberation mapping (RM) is an important technique for the study
+Reverberation mapping (RM) is a key technique for the study
 of active galactic nuclei (AGN). The technique is based on the temporal
@@
 
-RM is a observationally intensive, requiring observations of an AGNN
+RM is a observationally intensive, requiring observations of an AGN
 over a period of
@@
 is the normalised transfer function, is not equal to $c$ times the mean radius of the BLR
-distribution, $\bar{r} = \int \sqrt{x^2+y^2+z^2}\rho(x, y, z)\, d^3 \mathbf{x}$.
+matter distribution, $\bar{r} = \int \sqrt{x^2+y^2+z^2}\rho(x, y, z)\, d^3 \mathbf{x}$.
 Secondly, the mean lag $\bar{\tau}$ is not equivalent to the peak of the
@@
 \citep{loredo, kelly, extreme_deconvolution, 2012AJ....143...90S, 2012arXiv1208.3036L, 2013arXiv1310.5177B, 2013AJ....146....7B}.
-which allows us to measure
+which allows us to calculate the posterior distribution for hyperparameters
+which describe the typical lag, and the diversity of the lags.
 
@@
 inferences may be incorrect due to the implicit assumption that the prior for
-all of the $\{\theta_i\}$ is independent \citep{2013arXiv1310.5177B}.
+all of the $\btheta$ is independent \citep{2013arXiv1310.5177B}.
 A hierarchical model may be used to overcome this problem.
-Section~\ref{sec:single_object} describes the assumptions used for analysing
-data from a single AGN.
 
-In a hierarchical model, the prior for the parameters $\{\theta_i\}$ is created
+In a hierarchical model, the prior for the parameters $\btheta$ is created
 by introducing hyperparameters $\alpha$ such that the joint prior for $\alpha$
-and the $\{\theta_i\}$ is:
+and the $\btheta$ is:
 \begin{eqnarray}
-p(\alpha, \theta_i) &=& p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha)
+p(\alpha, \btheta) &=& p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha)
 \end{eqnarray}
-The implied prior on the $\{\theta_i\}$ parameters is then
+The implied prior on the $\btheta$ parameters is then
 \begin{eqnarray}
-p(\theta_i) &=& \int p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha) \, d\alpha
+p(\btheta) &=& \int p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha) \, d\alpha
 \end{eqnarray}
@@
 The posterior distribution for
-$\btheta = \{\theta_1, ..., \theta_N\}$ and the hyperparameters $\alpha$
+$\btheta$ and the hyperparameters $\alpha$
 given the data 
-$\bx = \{x_1, ..., x_N\}$, is then
+$\{x_1, ..., x_N\}$, is then
 \begin{eqnarray}
@@
 It is possible to consider the data for all $N$ objects as one big data set
-and infer the parameters of all objects simultaneously. However, this can be
+and infer the hyperparameters $\alpha$ and the parameters of all objects $\btheta$
+simultaneously. However, this can be
 computationally prohibitive. In some circumstances it is tractable to analyse
@@
 then post-process the results, reconstructing what the results of the
-hierarchical model would have been. In this letter we use this approach.
+hierarchical model would have been. In this letter we use this latter approach.
 
@@
 essentially an importance sampling approximation to the
-full hierarchical model.
+full hierarchical model. One drawback of this approach is that it implies an
+independent (non-hierarchical) prior on any per-object nuisance parameters,
+which can sometimes adversely affect the results \citep[e.g.][]{2013arXiv1310.5177B}.
 
@@
 units, as opposed to magnitudes, and consider $\bar{\tau}$ as
-the definition of ``the lag'' of the AGN.
+the definition of ``the lag'' of an AGN.
 
@@
 \frac{1}{b-a}, & \tau \in [a,b]\\
-0, & \textnormal{otherwise}s
+0, & \textnormal{otherwise}
 \end{array}\right.
@@
 \bar{\tau} &=& \int \tau \Psi(\tau) \, d\tau\\
-&=& \frac{1}{2}(b-a)
+&=& \frac{1}{2}(b-a).
 \end{eqnarray}
-
 Note that inferring $\bar{\tau}$ from the data requires that we
@@
 cross-correlation techniques and is similar to the approach used by
-\citep{2011ApJ...735...80Z}.
+\citet{2011ApJ...735...80Z}.
 

### 2013-11-01 Paper/ms.tex
Mention true values
Slight editing to conclusions

@@
 distribution was uniform over the area shown.
-The true solution is indicated by the white star symbol.\label{fig:posterior}}
+The true solution $(\mu = 0.867, \sigma = 0.157)$
+is indicated by the white star symbol.\label{fig:posterior}}
 \end{center}
@@
 \section{Conclusions}\label{sec:conclusions}
-Reverberation mapping is an important, yet observationally intensive,
-technique in studies of active galaxies. This has motivated substantial
+Reverberation mapping campaigns are observationally intensive, yet potentially
+very informative. This has led to
 research into RM data analysis techniques, as well as less costly observing

### 2013-11-01 Paper/ms.tex
Updated numbers

@@
 along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
-$\mu = 0.892 \pm 0.033$, and the prediction about $\log_{10}(\bar{\tau})$
-may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$. The Bayesian
+$\mu = 0.838 \pm 0.047$, and the prediction about $\log_{10}(\bar{\tau})$
+may be summarised as $\log_{10}(\bar{\tau}) = 0.838 \pm 0.215$. The Bayesian
 approach has clearly separated the uncertainty about $\mu$ from the diversity of the

### 2013-11-01 Paper/ms.tex
Updated a number

@@
 an inference on $\mu$, a hyperparameter describing the typical value of the lag,
-to within 0.033 dex (1-$\sigma$ uncertainty), whereas the stacked cross-correlation
+to within 0.047 dex (1-$\sigma$ uncertainty), whereas the stacked cross-correlation
 function had a FWHM of $\sim$ 0.25 dex. This is possible because a subset of

### 2013-12-03 Paper/ms.tex
mu --> m in the context of the AR(1) model

@@
 \begin{eqnarray}
-p(y_i | y_{i-1},  \mu, a, \beta) \sim \mathcal{N}
-\left(\mu + a\left(y_{i-1} - \mu\right), \beta^2\right)
+p(y_i | y_{i-1},  m, a, \beta) \sim \mathcal{N}
+\left(m + a\left(y_{i-1} - m\right), \beta^2\right)
 \end{eqnarray}
 for $i \geq 2$. This is the discrete AR(1) model from time series theory.
-$\mu$ describes the mean level of the continuum light curve, $\beta$ controls
+$m$ describes the mean level of the continuum light curve, $\beta$ controls
 the size of the short-term fluctuations, and $a$ controls the correlation
@@
 between $10^{-3}$ and $10^3$ flux units, a Cauchy(0, 100)
-prior for $\mu$ (the mean flux level of the AGN), a log-uniform prior for $b$
+prior for $m$ (the mean flux level of the AGN), a log-uniform prior for $b$
 (the upper limit of the transfer function) between $10^{-4}$ and $10^2$ days,

### 2013-12-03 Paper/ms.tex
Paragraph describing sims

@@
 To test our hierarchical model, and compare it to the stacked cross-correlation
-function, we simulated data from 100 AGN. The data for each object was
+function, we simulated data from a sample of 100 AGN. We assumed the
+continuum flux for each object fluctuates around a mean value $m = 50$ in
+arbitrary units. The variability timescales $L$ were simulated from a very
+broad log-uniform distribution (i.e. a uniform distribution for $\ln(L)$)
+with a lower limit of 100 days and an upper limit of $10,000$ days. The
+variability amplitudes $\beta$ were also simulated from a log-uniform
+distribution with lower limit of 0.2 flux units and an upper limit of 1 flux
+unit. This implies some objects are more variable than others, as is typical
+in reverberation mapping.
+
+The measured data for each of the 100 AGN was
 continuum flux measurements, once per day, for 100 days. The continuum fluxes

### 2013-12-03 Paper/ms.tex
More work on describing simulations

@@
 broad log-uniform distribution (i.e. a uniform distribution for $\ln(L)$)
-with a lower limit of 100 days and an upper limit of $10,000$ days. The
+with a lower limit of 10 days and an upper limit of $1,000$ days. The
 variability amplitudes $\beta$ were also simulated from a log-uniform
@@
 in reverberation mapping.
+
+Each object in the sample had its own transfer function parameters. The upper
+limit $b$ of the transfer function was simulated using a log-normal distribution
+with a median value of 10 days, and the standard deviation of $\ln(b)$ was
+0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
+$a$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
+approximated by a lognormal distribution with a median of 7.4 days and width
+(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157.
+The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
+all objects.
 
@@
 and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
-The flux of the line data is scaled to half that of the line data, and the
-measurement noise for the line data is 0.25, or 1\%. See Figure~\ref{fig:data}
-for three illustrative data sets from the sample.
+The flux of the line data is typically about half that of the continuum data
+(since $A=0.5$ for all objects), and the
+measurement noise for the line data is 0.25, or about 1\%.
+See Figure~\ref{fig:data} for three illustrative data sets from the sample.
 
@@
 The true solution $(\mu = 0.867, \sigma = 0.157)$
-is indicated by the white star symbol.\label{fig:posterior}}
+is indicated by the white star symbol. $\mu = 0.867$ corresponds to a typical
+lag of 7.4 days.\label{fig:posterior}}
 \end{center}
@@
 \end{figure}
+
+Note that our method for combining individual object results into an inference
+about the population (Section~\ref{sec:multiple}) assumes that the hierarchical
+prior applies to only a single parameter (in our case $\bar{\tau}$). If we
+incorporate additional information by using a hierarchical prior for the other
+model parameters, allowing us to detect (for example) that all of the response
+amplitudes $A$ were equal to 0.5, we may be able to make more accurate
+inferences. However, this would increase the complexity of the method and the
+computational expense.
 

### 2013-12-03 Paper/ms.tex
Acknowledge Stephen
Tweaks

@@
 
+\vspace{-0.5cm}
 \section{The Single Object Model}\label{sec:single_object}
@@
 approximated by a lognormal distribution with a median of 7.4 days and width
-(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157.
+(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157
+(these two quantities are the ones we will infer using the hierarchical model).
 The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
@@
 \begin{center}
-\includegraphics[scale=0.5]{Figures/data.eps}
+\includegraphics[scale=0.45]{Figures/data.eps}
 \caption{Three simulated data sets, out of a total of 100. It is difficult to
@@
 \begin{center}
-\includegraphics[scale=0.4]{Figures/ccf.eps}
+\includegraphics[scale=0.35]{Figures/ccf.eps}
 \caption{The stacked cross-correlation function of the simulated data.
@@
 \begin{center}
-\includegraphics[scale=0.5]{Figures/example_posteriors.eps}
+\includegraphics[scale=0.45]{Figures/example_posteriors.eps}
 \caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
-for three objects, each analysed separately with the single-object model. For
+for three objects whose data sets are shown in Figure~\ref{fig:data}.
+These posteriors were obtained by analysing each object separately with the
+single-object model. For
 the first object, there is a moderate ``detection'' of a lag at about 10 days
@@
 \begin{center}
-\includegraphics[scale=0.5]{Figures/posterior.eps}
+\includegraphics[scale=0.45]{Figures/posterior.eps}
 \caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
@@
 along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
-$\mu = 0.838 \pm 0.047$, and the prediction about $\log_{10}(\bar{\tau})$
+$\mu = 0.838 \pm 0.047$ (consistent with the known input value of
+$0.867 \approx \log_{10}(7.4)$),
+and the prediction about $\log_{10}(\bar{\tau})$
 may be summarised as $\log_{10}(\bar{\tau}) = 0.838 \pm 0.215$. The Bayesian
@@
 \begin{center}
-\includegraphics[scale=0.35]{Figures/posterior2.eps}
+\includegraphics[scale=0.3]{Figures/posterior2.eps}
 \caption{The marginal posterior distribution for $\mu$, the 
@@
 team provided helpful advice about the use of their software. BJB is partially
-supported by the Marsden Fund (Royal Society of New Zealand).
+supported by the Marsden Fund (Royal Society of New Zealand). We are grateful
+to the referee, Stephen Fine, for his helpful comments.
 

### 2013-12-03 Paper/ms.tex
Fixed error
More little edits

@@
 0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
-$a$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
+$b$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
 approximated by a lognormal distribution with a median of 7.4 days and width
@@
 The measured data for each of the 100 AGN was
-continuum flux measurements, once per day, for 100 days. The continuum fluxes
-for each object oscillate around a mean value of 50 in arbitrary units, and the
-standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
+continuum flux measurements, once per day, for 100 days. The standard deviation
+of the measurement noise is 1 flux unit (i.e. 2\%). The line data is measured on
 only two days, with times selected from a uniform distribution between $t=50$
@@
 (since $A=0.5$ for all objects), and the
-measurement noise for the line data is 0.25, or about 1\%.
+measurement noise for the line data is 0.25 flux units, or about 1\%.
 See Figure~\ref{fig:data} for three illustrative data sets from the sample.

### 2013-12-03 Paper/ms.tex
a --> k and other tweaks

@@
 
+\vspace{-0.5cm}
 \section{Combining Inferences About Multiple Objects}\label{sec:multiple}
@@
 \begin{eqnarray}
-p(y_i | y_{i-1},  m, a, \beta) \sim \mathcal{N}
-\left(m + a\left(y_{i-1} - m\right), \beta^2\right)
+p(y_i | y_{i-1},  m, k, \beta) \sim \mathcal{N}
+\left(m + k\left(y_{i-1} - m\right), \beta^2\right)
 \end{eqnarray}
@@
 $m$ describes the mean level of the continuum light curve, $\beta$ controls
-the size of the short-term fluctuations, and $a$ controls the correlation
-timescale (the timescale is given by $L = -1/\ln(a)$).
+the size of the short-term fluctuations, and $k$ controls the correlation
+timescale (the timescale itself is given by $L = -1/\ln(k)$).
 
 For the likelihood (or sampling distribution, really the prior for the data
-given the parameters) we made the conventional gaussian assumption:
+given the parameters) we made the conventional assumption of ``Gaussian noise'':
 \begin{eqnarray}
@@
 
+\vspace{-0.5cm}
 \section{Demonstration on Simulated Data}\label{sec:data}
@@
 The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
-all objects.
+all objects. Note that the distribution of the parameters of the 100 objects is
+not the same as the priors used when analysing them with the single-object model.
 
@@
 implied by the simple-object model, since we did not assign the prior directly
-to $\bar{\tau}$. The prior for $\bar{\tau}$ in the single-object model is
+to $\bar{\tau}$ but indirectly through $a$ and $b$.
+The prior for $\bar{\tau}$ in the single-object model is
 very well approximated by a log-uniform distribution.
@@
 
+\vspace{-0.5cm}
 \section{Conclusions}\label{sec:conclusions}
@@
 
+\vspace{-0.5cm}
 \section*{Acknowledgements}
